### 2019-10-14 article.tex
Initial SPIE template

\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}

\title{SPIE journal papers: sample manuscript showing style and formatting specifications}

\author[a]{First Author}
\author[a]{Second Author}
\author[b]{Third Author}
\author[a,b,*]{Fourth Author}
\affil[a]{University Name, Faculty Group, Department, Street Address, City, Country, Postal Code}
\affil[b]{Company Name, Street Address, City, Country, Postal Code}

\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

\begin{abstract}
This document shows the required format and appearance of a manuscript prepared for SPIE journals. It is prepared using LaTeX2e with the class file \texttt{spieman.cls}. Please note that the following journals encourage the use of \textbf{structured abstracts} in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the\textit{ Journal of Micro/Nanolithography, MEMS, and MOEMS}. Guidelines for structured abstracts are available on the journal website. Whether structured or single-paragraph, the abstract should contain approximately 200 words. It should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting and indexing databases, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period. The body of the manuscript should be double-spaced and fully justified.  
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Fourth author name,  \linkable{myemail@university.edu} }

\begin{spacing}{2}   % use double spacing for rest of manuscript

\section{Introduction}
\label{sect:intro}  % \label{} allows reference to this section
This document shows the format and appearance of a manuscript prepared for submission to an SPIE journal. Note that this template is only intended to be used as a guideline for author convenience. It is designed for optimum clarity and ease of reading for editors and reviewers, but the template does not reflect the final page layout of a published journal paper. Accepted papers are professionally typeset in XML according to the layout and design of the journal.

\subsection{Use of This Document}

This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.  The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it. Authors may use it as a template to create their own manuscript. While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.

\subsection{English}

Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example. In addition, good English usage is essential. Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced. Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}. SPIE authors will receive a 15\% discount off their services. A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission. Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.

\subsection{Page Setup and Fonts}

All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm). Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.

The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}. If this font is not available, use a similar serif font. The manuscript should not contain headers or footers. Pages should be numbered.

\begin{table}[ht]
\caption{Fonts sizes and styles.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
\hline\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
\hline 
\end{tabular}
\end{center}
\end{table}

\section{Parts of Manuscript}

This section describes the normal structure of a manuscript and how each part should be handled. The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.

\subsection{Title and Author Information}
\label{sect:title}
The article title appears left justified at the top of the first page. The title font is 16 pt., bold. The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized. Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.). The word ``novel'' should not appear in the title, as publication will imply novelty. Avoid the use of acronyms in the title, unless they are widely understood. Appendix A contains more about acronyms.

The list of authors immediately follows the title, 18 points below. The font is 12 pt., bold and the author names are left justified. The author affiliations and addresses follow the names, in 10-pt., normal font and left justified. For multiple affiliations, each affiliation should appear on a separate line. Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations. The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.

\subsection{Abstract}
The abstract should be a summary of the paper and not an introduction. Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance. Please note that the following journals encourage the use of \textbf{structured abstracts} in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}. Helpful guidelines for structured abstracts are available on the journal website. Whether structured or single-paragraph, the abstract should contain approximately 200 words.

\subsection{Keywords}
Up to eight keywords should be specified.

\subsection{Body of Paper}
The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.

To provide transition elements in your paper, it is important to refer back (or forward) to specific sections. Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out. When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.

At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).

\subsection{Footnotes}
Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided. If absolutely necessary, the footnote mark must come at the end of a sentence. To insert a footnote, use the {\verb|\footnote{}|} command.

\subsection{Appendices}
Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms. Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.

\subsection{Disclosures}
Conflicts of interest should be declared under a separate header, above Acknowledgments. If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest. For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}

\subsection{Acknowledgments}
Acknowledgments and funding information should be added after the conclusion, and before references. Include grant numbers and the full name of the funding body. The acknowledgments section does not have a section number.

\subsection{References}
The References section lists books, articles, and reports that are cited in the paper. This section does not have a section number. The references are numbered in the order in which they are cited. Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.  Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

The references are numbered in the order of their first citation. Citations to the references are made using superscripts, as demonstrated in the preceding paragraph. One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them. Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.

\subsubsection{Reference linking and DOIs}
A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet. The use of DOIs allows readers to easily access cited articles. Authors should include the DOI at the end of each reference in brackets if a DOI is available. See examples at the end of this manuscript. A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}. The inclusion of DOIs will facilitate reference linking and is highly recommended.

In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}. The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.

\subsection{Biographies}
A brief professional biography not to exceed 75 words may be provided for each author, if available. Biographies should be placed at the end of the paper, after the references. Personal information such as hobbies or birthplace/birthdate should not be included. Author photographs are not published.

\section{Section Formatting}
\label{sect:sections}
In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections. Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references. (Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.

Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style. The same goes for leading paragraphs of subsections and sub-subsections. Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation. There is no additional space between paragraphs. In LaTeX, paragraphs are separated by blank lines in the source file. Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

\subsection{Subsection Headings}
All important words in a subsection (level 1) header are capitalized. Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end. The heading is left justified and its font is 12 pt. italic.

\subsubsection{Sub-subsection headings}
The first word of a sub-subsection is capitalized. The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known). The heading is left justified and its font is 11 pt. italic.

\section{Figures and Tables}

\subsection{Figures}

Figures are numbered in the order in which they are called out in the text. They should appear in the document in numerical order and as close as possible to their first reference in the text. It may be necessary to move figures or tables around to enhance readability. LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.

Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered. Figure captions are centered below the figure or graph. Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt. font. See Fig.~\ref{fig:example} for an example.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{mcr3b.eps}
\end{tabular}
\end{center}
\caption 
{ \label{fig:example}
Example of a figure caption. } 
\end{figure}

Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.  In no case, should the article's text be wrapped around a figure. Figure~\ref{fig:example2} shows two side-by-side images. When a figure contains more than one image, the author must submit them as a single image file. Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.

\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
\\
(a) \hspace{5.1cm} (b)
\end{tabular}
\end{center}
\caption 
{ \label{fig:example2}
Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
\end{figure}

\subsection{Tables}
Tables are numbered in the order in which they are referenced. They should appear in the document in numerical order and as close as possible to their first reference in the text. It is preferable to have tables appear at the top or bottom of the page, if possible. Table captions are handled identically to those for figures, except that they appear above the table. See Table~\ref{tab:fonts} for an example.

\subsection{Multimedia}
Please refer to the multimedia section of the author guidelines (see link above) for specific requirements. The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4). The recommended maximum size for each multimedia file is 10-12 MB. Authors must insert a representative still image from the video file in the manuscript as a figure. The caption label will be linked by the publisher to the actual video file. The video may also be mentioned in an existing figure caption. Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.  The video number, file type, and file size should be included in parentheses at the end of the figure caption. See Figure \ref{vid:satellite} for an example.

\begin{video}
\begin{center}
{\includegraphics[height=5cm]{satellite.eps}}
\\
\end{center}
\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
\end{video}

\appendix    % this command starts appendixes

\section{Miscellaneous Formatting Details}
\label{sect:misc}
At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.

\subsection{Formatting Equations}
Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the field of view is
\begin{equation}
\label{eq:fov}
2 a = \frac{(b + 1)}{3c} \, ,
\end{equation}
where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma appears after the equation because the next line is a subordinate clause. If the equation ends the sentence, a period should follow the equation. The line following an equation should not be indented unless it is meant to start a new paragraph. Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise. Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..

\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.  The text of the theorem continues on the same line in normal, 10-pt. font, achieved in LaTeX using \verb|\footnotesize|.  For example,

\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}

% \disclosures 
\subsection*{Disclosures}
Conflicts of interest should be declared under a separate header. If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.

\acknowledgments 
This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%% References %%%%%

\bibliography{report}   % bibliography data in report.bib
\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst

%%%%% Biographies of authors %%%%%

\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering. He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.  He is the author of more than 50 journal papers and has written three book chapters. His current research interests include optical interconnects, holography, and optoelectronic systems. He is a member of SPIE.

\vspace{1ex}
\noindent Biographies and photographs of the other authors are not available.

\listoffigures
\listoftables

\end{spacing}
\end{document}

### 2020-05-29 article.tex
Transfer text into LaTeX document

@@
-\documentclass[12pt]{spieman}  % 12pt font required by SPIE;
-%\documentclass[a4paper,12pt]{spieman}  % use this instead for A4 paper
+\documentclass[12pt]{spieman}
 \usepackage{amsmath,amsfonts,amssymb}
@@
 
-\title{SPIE journal papers: sample manuscript showing style and formatting specifications}
+% Fix for Unicode characters in bibliography
+\usepackage{newunicodechar}
+\newunicodechar{κ}{$\kappa$}
+\newunicodechar{β}{$\beta$}
 
-\author[a]{First Author}
-\author[a]{Second Author}
-\author[b]{Third Author}
-\author[a,b,*]{Fourth Author}
-\affil[a]{University Name, Faculty Group, Department, Street Address, City, Country, Postal Code}
-\affil[b]{Company Name, Street Address, City, Country, Postal Code}
+% ---------------------------------------------------------------------------------------
+% BEGIN TITLE AND AUTHORS
+% ---------------------------------------------------------------------------------------
+\title{Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging}
 
+\author[a]{Colin T. Sullender}
+\author[b]{Fei He}
+\author[b,c]{Chong Xie}
+\author[b,c]{Lan Luan}
+\author[a,*]{Andrew K. Dunn}
+\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
+\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
+\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
+
+% ----------------------------------------------------------------------------------------
+% BEGIN DOCUMENT
+% ----------------------------------------------------------------------------------------
 \renewcommand{\cftdotsep}{\cftnodots}
@@
 
+% ----------------------------------------------------------------------------------------
+% BEGIN ABSTRACT
+% ----------------------------------------------------------------------------------------
 \begin{abstract}
-This document shows the required format and appearance of a manuscript prepared for SPIE journals.
-It is prepared using LaTeX2e with the class file \texttt{spieman.cls}.
-Please note that the following journals encourage the use of \textbf{structured abstracts} in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the\textit{ Journal of Micro/Nanolithography, MEMS, and MOEMS}.
-Guidelines for structured abstracts are available on the journal website.
-Whether structured or single-paragraph, the abstract should contain approximately 200 words.
-It should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting and indexing databases, it should be self-contained (i.e., no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-A list of up to eight keywords should immediately follow, with the keywords separated by commas and ending with a period.
-The body of the manuscript should be double-spaced and fully justified.
+Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology.
+In this paper, we characterize the impact of isoflurane during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI) of cerebral blood flow (CBF).
+We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions.
+Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchymal perfusion.
+These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
 \end{abstract}
@@
 % Include a list of up to six keywords after the abstract
-\keywords{optics, photonics, light, lasers, journal manuscripts, LaTeX template}
+\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, awake imaging, anesthesia}
 
 % Include email contact information for corresponding author
-{\noindent \footnotesize\textbf{*}Fourth author name,  \linkable{myemail@university.edu} }
+{\noindent \footnotesize\textbf{*}Andrew K. Dunn,  \linkable{adunn@utexas.edu} }
 
@@
 
+% ----------------------------------------------------------------------------------------
+% BEGIN INTRODUCTION SECTION
+% ----------------------------------------------------------------------------------------
 \section{Introduction}
-\label{sect:intro}  % \label{} allows reference to this section
-This document shows the format and appearance of a manuscript prepared for submission to an SPIE journal.
-Note that this template is only intended to be used as a guideline for author convenience.
-It is designed for optimum clarity and ease of reading for editors and reviewers, but the template does not reflect the final page layout of a published journal paper.
-Accepted papers are professionally typeset in XML according to the layout and design of the journal.
+\label{sect:introduction}
 
-\subsection{Use of This Document}
+The use of general anesthesia during neuroimaging is ubiquitous across many animal models despite systemic effects on neurophysiological state and cardiovascular function \cite{Slupe:2018ea}.
+Volatile inhalation anesthetics, such as the halogenated ether isoflurane \cite{Eger:1981ia}, are commonly utilized to immobilize animals during imaging while allowing for fine control over the depth of anesthesia and consciousness.
+However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Strebel:1995uh,Iida:1998th}.
+Isoflurane also conveys potential neuroprotective effects that reduce and delay the severity of cerebral ischemia \cite{Kitano:2007ia,Kawaguchi:2000id,Sakai:2007wc,Li:2013ip,Lu:2017bo}.
+These effects can mask the benefits of prospective neuroprotective therapeutics or interventions and confound the outcomes of long-term studies \cite{Kapinya:2002ua,Seto:2014ga}.
+For these reasons and more \cite{Gao:2017tw}, there is a growing effort within the neuroscience community to transition to un-anesthetized awake animal models in order to more accurately interpret neurophysiological and behavioral experiments and more readily translate findings to awake human physiology.
 
-This document is prepared using LaTeX2e\cite{Lamport94,Goossens97} with the class file {\ttfamily spieman.cls}.
-The LaTeX source file used to create this document is {\ttfamily article.tex}, which contains important formatting information embedded in it.
-Authors may use it as a template to create their own manuscript.
-While LaTeX properly handles most formatting issues, the author may occasionally need to intervene to obtain a satisfactorily  formatted manuscript.
+There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics.
+Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry (LDF), and intrinsic signal optical imaging (ISOI) have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
+Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
+Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
+To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
 
-\subsection{English}
+In this paper, we present multi-exposure speckle imaging (MESI) of cerebral blood flow in awake mice during the induction of general anesthesia with isoflurane.
+The MESI technique \cite{Parthasarathy:2008el} provides a more robust estimate of large changes in flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo} and enables the chronic tracking of CBF \cite{Kazmi:2013hp}.
+We highlight the large anatomical and physiological changes to cortical hemodynamics in response to isoflurane with wide-field imagery across multiple imaging sessions and animals.
+Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible.
 
-Authors are strongly encouraged to follow the principles of sound technical writing, as found in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-In addition, good English usage is essential.
-Authors whose native language is not English may wish to collaborate with a colleague whose English skills are more advanced.
-Alternatively, you may wish to have your manuscript professionally edited prior to submission by Editage, our recommended independent editorial service: \linkable{https://www.editage.com/spie/}.
-SPIE authors will receive a 15\% discount off their services.
-A spell checker can be helpful to discover misspelled words, but authors should also proofread their papers carefully prior to submission.
-Manuscripts that do not meet acceptable English standards or lack clarity may be rejected.
+% ----------------------------------------------------------------------------------------
+% BEGIN METHODS SECTION
+% ----------------------------------------------------------------------------------------
+\section{Methods}
+\label{sect:methods}
 
-\subsection{Page Setup and Fonts}
+\subsection{Multi-Exposure Speckle Imaging (MESI)}
+A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a.
+MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego) and relayed to illuminate the craniotomy at an oblique angle.
+The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm.
+Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of ~2.5 MESI frames-per-second.
+The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
+The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.
 
-All text and figures, including footnotes, must fit inside a text area 6.5 in.\ wide by 9 in.\ high (16.51 by 22.86 cm).
-Manuscripts must be formatted for US letter paper, on which the margins should be 1 in.\ (2.54 cm) on the top, 1 in.\ on the bottom, and 1 in.\ on the left and right.
+The 15 raw intensity images were converted to spatial speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
+%
+% Equation 1 - MESI Equation
+\begin{equation}
+    \label{eq:mesi}
+    K(T,\tau_c) =
+        \left(
+        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
+        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
+        \beta(1 - \rho)^2 +
+        \nu_{ne} +
+        \nu_{noise}
+        \right)^{1/2}
+\end{equation}
 
-The Times New Roman font is used throughout the manuscript, in the sizes and styles shown in Table~\ref{tab:fonts}.
-If this font is not available, use a similar serif font.
-The manuscript should not contain headers or footers.
-Pages should be numbered.
+\noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu_{noise}$ represents exposure-independent instrument noise and nonergodic variances.
+Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:2005} using a custom program written in C.
 
-\begin{table}[ht]
-\caption{Fonts sizes and styles.} 
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Document entity & Brief description  \\
-\hline\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names & 12 pt., bold, left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author affiliations & 10 pt., left justified   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Abstract & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Keywords & 10 pt.  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 12 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 12 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 11 pt., italic, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 12 pt. \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions &  10 pt. \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table}
+Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}.
+Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}.
+This is achieved by scaling the fitted $ICT$ value by the caliber of the vessel ($d_{vessel}$) in order to obtain an estimate of "vascular flux” that accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
+This paper utilizes the “flux” metric (arbitrary units) for all vascular measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
 
-\section{Parts of Manuscript}
+% ----------------------------------------------------------------------------------------
 
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
+\subsection{Animal Preparation}
+Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
+Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts).
+Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific).
+Mice were placed supine in a stereotaxic frame (Kent Scientific) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure.
+The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates.
+A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
+A 3 mm round cover glass (\#1, World Precision Instruments) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
+Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments) was deposited to bond the glass to the skull.
+A layer of C\&B-Metabond (Parkell Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure.
+A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements.
+The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging.
+They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.
 
-\subsection{Title and Author Information}
-\label{sect:title}
-The article title appears left justified at the top of the first page.
-The title font is 16 pt., bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Do not begin titles with articles (for example, a, an, the) or prepositions (for example, on, by, etc.).
-The word ``novel'' should not appear in the title, as publication will imply novelty.
-Avoid the use of acronyms in the title, unless they are widely understood.
-Appendix A contains more about acronyms.
+Mice were housed 1-4 per cage in a conventional vivarium maintained at 20 $^\circ$C on 12-hour light-to-dark cycles (07:00 to 19:00).
+All subjects received standard cage supplements (e.g.
+cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}.
+All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin (AUP-2018-00021).
 
-The list of authors immediately follows the title, 18 points below.
-The font is 12 pt., bold and the author names are left justified.
-The author affiliations and addresses follow the names, in 10-pt., normal font and left justified.
-For multiple affiliations, each affiliation should appear on a separate line.
-Superscript letters (a, b, c, etc.) should be used to associate multiple authors with their respective affiliations.
-The corresponding author should be identified with an asterisk, and that person's email address should be provided below the keywords.
+% ----------------------------------------------------------------------------------------
 
-\subsection{Abstract}
-The abstract should be a summary of the paper and not an introduction.
-Because the abstract may be used in abstracting journals, it should be self-contained (that is, no numerical references) and substantive in nature, presenting concisely the objectives, methodology used, results obtained, and their significance.
-Please note that the following journals encourage the use of \textbf{structured abstracts} in manuscript submissions: \textit{Neurophotonics}, the \textit{Journal of Biomedical Optics}, and the \textit{Journal of Micro/Nanolithography, MEMS, and MOEMS}.
-Helpful guidelines for structured abstracts are available on the journal website.
-Whether structured or single-paragraph, the abstract should contain approximately 200 words.
+\subsection{Awake-to-Anesthetized Blood Flow Measurements}
 
-\subsection{Keywords}
-Up to eight keywords should be specified.
+Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
+The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}).
+A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%).
+Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2\% to induce anesthesia.
+After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function.
+After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
+The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames.
+The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage.
+Each subject underwent three imaging sessions with at least one full day of recovery between each session.
 
-\subsection{Body of Paper}
-The body of the paper consists of numbered sections that present the main findings. These sections should be organized to best present the material.
+An additional subject ($n = 1$) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
+Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery.
+The four repeated imaging sessions for this subject were spaced at least one week apart to avoid any complications from extended anesthesia exposure.
 
-To provide transition elements in your paper, it is important to refer back (or forward) to specific sections.
-Such references are made by indicating the section number, for example, ``In Sec.\ 2 we showed...'' or ``Section 2.1 contained a description...'' If the word Section, Reference, Equation, or Figure starts a sentence, it is spelled out.
-When occurring in the middle of a sentence, these words are abbreviated Sec., Ref., Eq., and Fig.
+% ----------------------------------------------------------------------------------------
+% BEGIN RESULTS SECTION
+% ----------------------------------------------------------------------------------------
+\section{Results}
+\label{sect:results}
 
-At the first occurrence of an acronym, spell it out followed by the acronym in parentheses, for example, charge-coupled diode (CCD).
+The systematic changes caused by general anesthesia are shown in Fig.~\ref{fig:system_image}b and Video 1.
+The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in cerebral blood flow caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
+Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
+These large alterations to the vasculature precluded the generation of full-field relative flow change maps.
 
-\subsection{Footnotes}
-Textual footnotes should be used rarely to present important documentary or explanatory material whose inclusion in the text would be distracting.\footnote{Example of a footnote.} Due to problems with HTML display, use of footnotes should generally be avoided.
-If absolutely necessary, the footnote mark must come at the end of a sentence.
-To insert a footnote, use the {\verb|\footnote{}|} command.
-
-\subsection{Appendices}
-Brief appendices may be included when necessary, such as derivations of equations, proofs of theorems, and details of algorithms.
-Equations and figures appearing in appendices should continue sequential numbering from earlier in the paper.
-
-\subsection{Disclosures}
-Conflicts of interest should be declared under a separate header, above Acknowledgments.
-If the authors have no competing interests to declare, then a statement should be included declaring no conflicts of interest.
-For assistance generating a disclosure statement, see the form available from  the International Committee of Medical Journal Editors website: \linkable{http://www.icmje.org/conflicts-of-interest/}
-
-\subsection{Acknowledgments}
-Acknowledgments and funding information should be added after the conclusion, and before references.
-Include grant numbers and the full name of the funding body.
-The acknowledgments section does not have a section number.
-
-\subsection{References}
-The References section lists books, articles, and reports that are cited in the paper.
-This section does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
-
-The reference list at the end of this document is created using BibTeX, which looks through the file {\ttfamily report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\ttfamily spiejour.bst}, as specified in the \\ \verb|\bibliographystyle{spiejour}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors (initials plus last name), book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-Journal-article references \cite{Metropolis53,Harris06} include the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers or citation identifier, and year.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), editors (if appropriate), volume title (in italics), volume number if applicable (in bold), inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-The references are numbered in the order of their first citation.
-Citations to the references are made using superscripts, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, for example, ``as shown in Ref.~\citenum{Metropolis53} ...''  Two or more references should be separated by a comma with no space between them.
-Multiple sequential references should be displayed with a dash between the first and last numbers \cite{Alred03,Perelman97,Lamport94,Goossens97,Metropolis53}.
-
-\subsubsection{Reference linking and DOIs}
-A Digital Object Identifier (DOI) is a unique alphanumeric string assigned to a digital object, such as a journal article or a book chapter, that provides a persistent link to its location on the internet.
-The use of DOIs allows readers to easily access cited articles.
-Authors should include the DOI at the end of each reference in brackets if a DOI is available.
-See examples at the end of this manuscript.
-A free DOI lookup service is available from CrossRef at \\\linkable{http://www.crossref.org/freeTextQuery/}.
-The inclusion of DOIs will facilitate reference linking and is highly recommended.
-
-In the present LaTeX template, the author needs to add the DOI reference by including it in a ``note'' in the bibliography file, as shown in the file {\verb+report.bib+}, for example, \\ {\verb+note = "[doi:10.1117/12.154577]"+}.
-The DOI may be used by the reader to locate that document with the link: {\verb+http://dx.doi.org10.1117/12.154577+}.
-
-\subsection{Biographies}
-A brief professional biography not to exceed 75 words may be provided for each author, if available.
-Biographies should be placed at the end of the paper, after the references.
-Personal information such as hobbies or birthplace/birthdate should not be included.
-Author photographs are not published.
-
-\section{Section Formatting}
-\label{sect:sections}
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
-Sections will be numbered sequentially, starting with the first section after the abstract, except for the acknowledgments and references.
-(Note that numbering of section headings is not required, but the numbering must be consistent if used.) All section headings should be left justified.
-
-Main section headings are in 12-pt. bold font, left-justified and in title case, where important words are capitalized.
-
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 0.2-in (5 mm) indentation.
-There is no additional space between paragraphs.
-In LaTeX, paragraphs are separated by blank lines in the source file.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
-
-\subsection{Subsection Headings}
-All important words in a subsection (level 1) header are capitalized.
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section, without a period at the end.
-The heading is left justified and its font is 12 pt.
-italic.
-
-\subsubsection{Sub-subsection headings}
-The first word of a sub-subsection is capitalized.
-The rest of the text is not capitalized, except for proper names and acronyms (the latter should only be used if well known).
-The heading is left justified and its font is 11 pt.
-italic.
-
-\section{Figures and Tables}
-
-\subsection{Figures}
-
-Figures are numbered in the order in which they are called out in the text.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It may be necessary to move figures or tables around to enhance readability.
-LaTeX will attempt to place figures at the top or bottom of a page in which they are first referenced.
-
-Figures, along with their captions, should be separated from the main text by  0.2 in.\ or 5 mm and centered.
-Figure captions are centered below the figure or graph.
-Figure captions start with the abbreviation ``Fig'' in front of the figure number, followed by a period, and the text in 10-pt.
-font.
-See Fig.~\ref{fig:example} for an example.
-
+% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
 \begin{figure}
@@
         \begin{tabular}{c}
-\includegraphics[height=5.5cm]{mcr3b.eps}
+            \includegraphics[width=6.25in]{Figure1.pdf}
         \end{tabular}
     \end{center}
-\caption 
-{ \label{fig:example}
-Example of a figure caption. } 
+    \caption {
+        \label{fig:system_image}
+        (a) MESI system schematic with 2x magnification.
+L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs).
+(b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
+    }
 \end{figure}
 
-Authors may wish to create figures consisting of two or more images, in which case, they should be neatly arranged in a rectangular array.
-In no case, should the article's text be wrapped around a figure.
-Figure~\ref{fig:example2} shows two side-by-side images.
-When a figure contains more than one image, the author must submit them as a single image file.
-Further details about figure formatting can be found in the author guidelines for each specific SPIE journal: \\
-\linkable {https://www.spiedigitallibrary.org/journals/journal-authors}.
+The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session.
+The open source image registration toolbox Elastix \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery in order to account for motion-related displacements.
+A central moving average filter ($k = 5$) was also applied to smooth the fitted data for presentation.
+The change in diameter of the two vessels (R1 and R2) was estimated using the full-width at half-maximum (FWHM) of a Gaussian fit to the vascular cross-sections extracted from the 5 ms exposure speckle contrast frames (Fig.~\ref{fig:acute}b).
+The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\%.
+This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c).
+The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%.
+Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) exhibit the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to anesthesia.
 
+% Figure 2 - Extended Awake to Anesthetized Measurements
 \begin{figure}
@@
         \begin{tabular}{c}
-\includegraphics[height=5.5cm]{fig2.eps}  % fig2 includes two images 
-\\
-(a) \hspace{5.1cm} (b)
+            \includegraphics[width=6.25in]{Figure2.pdf}
         \end{tabular}
     \end{center}
-\caption 
-{ \label{fig:example2}
-Example of a figure containing multiple images: (a) sun and (b) blob. Figures containing multiple images must be submitted to SPIE as a single image file.} 
+    \caption {
+        \label{fig:acute}
+        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis.
+Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
+Timecourses of (b) vessel caliber and (c) relative change in blood flow within the regions over an extended two-hour imaging session.
+The vertical dashed line indicates the beginning of anesthesia induction.
+The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
+Repeated measurements of (d) vessel caliber, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four days (mean $\pm$ sd).
+    }
 \end{figure}
 
-\subsection{Tables}
-Tables are numbered in the order in which they are referenced.
-They should appear in the document in numerical order and as close as possible to their first reference in the text.
-It is preferable to have tables appear at the top or bottom of the page, if possible.
-Table captions are handled identically to those for figures, except that they appear above the table.
-See Table~\ref{tab:fonts} for an example.
+The repeatability of these measurements are further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}.
+Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each.
+Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the hemodynamics.
+On average, vessel width increased by 10-20\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1\%) and therefore a smaller increase in vascular flux (+60\%).
+The perfusion of parenchymal regions increased on average by at least 50\% across all subjects.
 
-\subsection{Multimedia}
-Please refer to the multimedia section of the author guidelines (see link above) for specific requirements.
-The following types of multimedia files are accepted: QuickTime Non-Streaming video (.qt or .mov), MPEG (.mpg or .mp4).
-The recommended maximum size for each multimedia file is 10-12 MB.
-Authors must insert a representative still image from the video file in the manuscript as a figure.
-The caption label will be linked by the publisher to the actual video file.
-The video may also be mentioned in an existing figure caption.
-Multimedia files are treated in the same manner as figures and they will be numbered sequentially with normal figures.
-The video number, file type, and file size should be included in parentheses at the end of the figure caption.
-See Figure \ref{vid:satellite} for an example.
+% Figure 3 - Awake to Anesthetized Results Summary
+\begin{figure}
+    \begin{center}
+        \begin{tabular}{c}
+            \includegraphics[width=6.25in]{Figure3.pdf}
+        \end{tabular}
+    \end{center}
+    \caption {
+        \label{fig:summary}
+        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis.
+Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
+Each row of charts depicts average vessel caliber, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
+    }
+\end{figure}
 
-\begin{video}
-\begin{center}
-{\includegraphics[height=5cm]{satellite.eps}}
-\\
-\end{center}
-\caption{\label{vid:satellite}This satellite is a still image from Video 1 (Video 1, MPEG, 2.5 MB).}
-\end{video}
+% ----------------------------------------------------------------------------------------
+% BEGIN DISCUSSION SECTION
+% ----------------------------------------------------------------------------------------
+\section{Discussion}
+\label{sect:discussion}
 
-\appendix    % this command starts appendixes
+The systemic effects of isoflurane undermine the reliability of neurophysiological and behavioral studies because anesthesia is a fundamentally unnatural physiological state \cite{Gao:2017tw}.
+Imaging blood flow on the cortical surface with MESI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
+On average, the vasodilation caused by isoflurane increased vessel diameter by 18 $\pm$ 13\% across all trials with large vessel-to-vessel variation but small day-to-day variation (Fig.~\ref{fig:summary}).
+Direct microscope measurements in fentanyl- and nitrous oxide-anesthetized rats documented a 17\% increase in arteriolar diameter and 6\% increase in venule diameter after the topical application of isoflurane \cite{Koenig:1994rn}.
+Similar measurements in pentobarbital-anesthetized dogs observed 10-28\% increases in the diameter of small arterioles following the inhalation of isoflurane \cite{Iida:1998th}.
+Both studies found that isoflurane dilated arterioles in a concentration-dependent manner.
 
-\section{Miscellaneous Formatting Details}
-\label{sect:misc}
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph. In a LaTeX source file, a linebreak is created with \verb|\\|.
+Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials.
+Even vessels that experienced only minimal vasodilation, such as R2 for Subject 1 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow.
+Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals.
+A lone study using LDF found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
+However, because large blood vessels were avoided, the LDF likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI.
+The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by LDF, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.
 
-\subsection{Formatting Equations}
-Equations may appear inline with the text, if they are simple, short, and not of major importance; for example, $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the field of view is
-\begin{equation}
-\label{eq:fov}
-2 a = \frac{(b + 1)}{3c} \, ,
-\end{equation}
-where $a$ is the ...''  Principal equations are numbered, with the equation number placed within parentheses and right justified.
+Within the parenchyma, perfusion increased on average by 92 $\pm$ 35\% across all trials after only 20 minutes of isoflurane exposure.
+The reduced variability compared to the vascular measurements is likely a byproduct of the more homogenous structure of the unresolvable capillaries within the parenchyma.
+fMRI measurements in isoflurane-anesthetized rats have reported $\sim$50\% increases in global CBF with the cerebral cortex experiencing the smallest regional increase (20\%) compared to the awake state \cite{Sicard:2003dj}.
+However, these numbers are not directly comparable because fMRI samples a much larger volume of the brain than MESI, which has both a smaller field of view and only penetrates several hundred microns into the cortex.
 
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma appears after the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
+While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj, Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}.
+Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a range of flow rates \cite{Parthasarathy:2008el}.
+Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the visible surface vasculature.
+Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:acute}c would have measured only a 140\% increase in the large vessel instead of 267\%.
+The repeatability of the day-to-day measurements further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
 
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:fov}) shows ...'' or ``Combining Eqs.~(2) and (3), we obtain...'' Note that the word ``Equation'' is spelled out if it begins a sentence, but is abbreviated as ``Eq.'' otherwise.
-Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks, for example between ``Eq.'' and the following equation number..
+The effects of isoflurane fundamentally undermine the imaging of cortical hemodynamics in the normal physiological state.
+Blood flow imaging techniques such as LSCI, LDF, and fMRI require greater sensitivity because of the suppression of the hemodynamic response \cite{Takuwa:2012ee} and measure a delayed neurovascular coupling \cite{Pisauro:2013cx}.
+Anatomical imaging with two-photon microscopy only captures heavily-dilated vasculature unrepresentative of the awake resting state \cite{Lyons:2016bd}.
+The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:acute}b.
+This may result in extended imaging sessions documenting disparate anatomies and physiologies between the beginning and conclusion of an experiment.
 
-\subsection{Formatting Theorems}
+% ----------------------------------------------------------------------------------------
 
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified, and followed by a period.
-The text of the theorem continues on the same line in normal, 10-pt.
-font, achieved in LaTeX using \verb|\footnotesize|.
-For example,
+\subsection{Limitations}
 
-\vspace{2ex}\noindent{\footnotesize\textbf{Theorem 1.} For any unbiased estimator...}
+The impact of repeated exposure to isoflurane was not examined in this study.
+Previous work has found that it can impair synaptic plasticity in the basolateral amygdala \cite{Long:2016ri} and cause persistent motor deficits via structural changes to the corpus callosum \cite{Bajwa:2018ri}.
+The one day interval between imaging sessions may not have been sufficient to avoid these effects despite only 20 minutes of isoflurane exposure.
+Because the experiment imaged the induction of general anesthesia from the awake state, tracheal intubation for mechanical ventilation was not an option.
+This may result in breathing variability that impacts the systemic hemodynamics and complicates comparisons with other studies that had mechanical control of ventilation.
+Since varying the isoflurane dosage was the only method of regulating breathing stability, the concentration dependent effects of isoflurane may have also influenced the results \cite{Masamoto:2009dd,Li:2014eh}.
 
-% \disclosures 
+While image registration can help maintain the spatial alignment of data across an experiment, it is unable to decouple the effects of animal motion from the underlying blood flow.
+Even with the head fully restrained, walking and grooming both cause subtle brain movements that manifest as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:acute}c.
+While these fluctuations may characterize real hemodynamic responses, it is difficult to isolate them from systemic animal motion.
+A simple solution might be the addition of an external sensor to the treadmill \cite{Dombeck:2007gr} to exclude timepoints when the animal is actively moving.
+However, a more refined awake imaging system that minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI or other dynamic light scattering imaging techniques.
+
+% ----------------------------------------------------------------------------------------
+% BEGIN CONCLUSION SECTION
+% ----------------------------------------------------------------------------------------
+\section{Conclusion}
+\label{sect:conclusion}
+
+We have used MESI to image CBF during the induction of general anesthesia with isoflurane in head-restrained mice.
+The vasodilatory effects of isoflurane caused large anatomical and physiological changes that were drastically different from the awake state.
+These increases in vessel size and blood flow were repeatable across multiple imaging sessions in the same subjects.
+This study also demonstrated that the MESI technique can be readily used for chronic awake imaging and allows for direct day-to-day and animal-to-animal comparisons of blood flow.
+These results provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.
+
+% ----------------------------------------------------------------------------------------
+% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
+% ----------------------------------------------------------------------------------------
 \subsection*{Disclosures}
-Conflicts of interest should be declared under a separate header.
-If the authors have no relevant financial interests in the manuscript and no other potential conflicts of interest to disclose, a statement to this effect should also be included in the manuscript.
+A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.
+
+\subsection*{Author Contributions}
+C.T.S.
+constructed the imaging system, conceived the experiments, acquired the data, analyzed the results, and wrote the manuscript.
+F.H.
+performed the animal surgeries.
+C.X., L.L., and A.K.D.
+supervised the project.
+All authors contributed to the manuscript revisions.
 
 \acknowledgments
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
+This study was supported by the National Institutes of Health...
 
-%%%%% References %%%%%
+% ----------------------------------------------------------------------------------------
+% BEGIN BIBLIOGRAPHY
+% ----------------------------------------------------------------------------------------
+\bibliography{bibliography.bib}
+\bibliographystyle{spiejour} % SPIE bibliography style
 
-\bibliography{report}   % bibliography data in report.bib
-\bibliographystyle{spiejour}   % makes bibtex use spiejour.bst
+% ----------------------------------------------------------------------------------------
+% AUTHOR BIOGRAPHIES
+% ----------------------------------------------------------------------------------------
+\vspace{1ex}
+\vspace{2ex}\noindent\textbf{Colin T.
+Sullender} received his PhD in biomedical engineering from the University of Texas at Austin in 2018.
+Currently, he is a postdoctoral research fellow working with Dr.
+Andrew Dunn in the Functional Optical Imaging Laboratory (FOIL) at the University of Texas.
+His research focuses on the continued development and clinical translation of the laser speckle contrast imaging technique.
 
-%%%%% Biographies of authors %%%%%
+\vspace{2ex}\noindent\textbf{Fei He} received his PhD in optical engineering from the Chinese Academy of Sciences.
+Currently, he is a postdoctoral research fellow working with Dr.
+Lan Luan in the Luan Laboratory of Integrative Neural Interface at Rice University.
 
-\vspace{2ex}\noindent\textbf{First Author} is an assistant professor at the University of Optical Engineering.
-He received his BS and MS degrees in physics from the University of Optics in 1985 and 1987, respectively, and his PhD degree in optics from the Institute of Technology in 1991.
-He is the author of more than 50 journal papers and has written three book chapters.
-His current research interests include optical interconnects, holography, and optoelectronic systems.
-He is a member of SPIE.
+\vspace{2ex}\noindent\textbf{Chong Xie} is an Associate Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative.
+His research focuses on the development of advanced nanoelectronic devices for probing and manipulating neural systems.
 
-\vspace{1ex}
-\noindent Biographies and photographs of the other authors are not available.
+\vspace{2ex}\noindent\textbf{Lan Luan} is an Assistant Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative.
+Her research focuses on the development of multimodal neural interfaces that combine electrical, optical, and other technologies to monitor and manipulate brain activity.
 
+\vspace{2ex}\noindent\textbf{Andrew K.
+Dunn} is the Donald J.
+Douglass Centennial Professor of Engineering in the Department of Biomedical Engineering at the University of Texas at Austin and the Director of the Center for Emerging Imaging Technologies.
+His research focuses on the development of innovative optical imaging techniques for studying the brain.
+
+% ----------------------------------------------------------------------------------------
+% FIGURE AND TABLE LISTS
+% ----------------------------------------------------------------------------------------
 \listoffigures
-\listoftables
 
@@
 \end{document}
+
+% ----------------------------------------------------------------------------------------
+% END
+% ----------------------------------------------------------------------------------------

### 2020-06-05 article.tex
Edits and implemented Andy's changes

@@
 \author[a]{Colin T. Sullender}
+\author[a]{Lisa M. Richards}
 \author[b]{Fei He}
@@
 Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology.
-In this paper, we characterize the impact of isoflurane during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI) of cerebral blood flow (CBF).
+In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI).
 We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions.
@@
 There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics.
-Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry (LDF), and intrinsic signal optical imaging (ISOI) have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
+Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
 Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
@@
 A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a.
-MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego) and relayed to illuminate the craniotomy at an oblique angle.
+MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle.
 The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm.
-Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of ~2.5 MESI frames-per-second.
+Fifteen camera exposures ranging between 50 $\mu$s and 80 ms {Parthasarathy:2008el, Atchia:2013ep, Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
 The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
@@
 
-The 15 raw intensity images were converted to spatial speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
+The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
 %
@@
 Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}.
-This is achieved by scaling the fitted $ICT$ value by the caliber of the vessel ($d_{vessel}$) in order to obtain an estimate of "vascular flux” that accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
-This paper utilizes the “flux” metric (arbitrary units) for all vascular measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
+This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
+This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
 
@@
 \subsection{Animal Preparation}
-Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
-Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts).
-Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific).
-Mice were placed supine in a stereotaxic frame (Kent Scientific) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure.
+
+Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
+Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.).
+Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.).
+Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure.
 The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates.
-A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
-A 3 mm round cover glass (\#1, World Precision Instruments) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
-Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments) was deposited to bond the glass to the skull.
-A layer of C\&B-Metabond (Parkell Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure.
+A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
+A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
+Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull.
+A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure.
 A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements.
@@
 cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}.
-All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin (AUP-2018-00021).
+All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.
 
@@
 A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%).
-Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2\% to induce anesthesia.
+Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia.
 After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function.
@@
 Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery.
-The four repeated imaging sessions for this subject were spaced at least one week apart to avoid any complications from extended anesthesia exposure.
+The timing of the anesthesia induction is identical to the protocol described above.
+The four repeated imaging sessions for this subject were spaced at least one week apart to minimize any complications from extended anesthesia exposure.
+
+% ----------------------------------------------------------------------------------------
+
+\subsection{Data Processing}
+
+While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts.
+The induction of general anesthesia also causes a major change in posture that can result in lateral displacements of the brain relative to the skull.
+In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery prior to fitting Eq.~(\ref{eq:mesi}).
+The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second.
+$ICT$ timecourses spanning the entire imaging session were also extracted from the fitted data from both vascular and parenchymal regions of interest.
+
+In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) was estimated using the 5 ms exposure speckle contrast frames.
+Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution.
+Because LSCI is most sensitive to moving scatterers, i.e.
+erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel.
+The vascular flux was then computed by scaling MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}.
+Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.
 
@@
 
-The systematic changes caused by general anesthesia are shown in Fig.~\ref{fig:system_image}b and Video 1.
-The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in cerebral blood flow caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
+The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1.
+The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
 Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
-These large alterations to the vasculature precluded the generation of full-field relative flow change maps.
+These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.
 
@@
         \label{fig:system_image}
-        (a) MESI system schematic with 2x magnification.
-L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs).
+        (a) MESI system schematic with 2x magnification: L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
 (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
@@
 The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session.
-The open source image registration toolbox Elastix \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery in order to account for motion-related displacements.
-A central moving average filter ($k = 5$) was also applied to smooth the fitted data for presentation.
-The change in diameter of the two vessels (R1 and R2) was estimated using the full-width at half-maximum (FWHM) of a Gaussian fit to the vascular cross-sections extracted from the 5 ms exposure speckle contrast frames (Fig.~\ref{fig:acute}b).
-The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\%.
+The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b.
+The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure.
 This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c).
 The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%.
-Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) exhibit the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to anesthesia.
+The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes.
+The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size.
+Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
 
@@
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
-Timecourses of (b) vessel caliber and (c) relative change in blood flow within the regions over an extended two-hour imaging session.
+Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session.
 The vertical dashed line indicates the beginning of anesthesia induction.
 The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
-Repeated measurements of (d) vessel caliber, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four days (mean $\pm$ sd).
+Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd).
     }
@@
 
-The repeatability of these measurements are further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}.
+The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}.
 Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each.
-Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the hemodynamics.
-On average, vessel width increased by 10-20\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1\%) and therefore a smaller increase in vascular flux (+60\%).
-The perfusion of parenchymal regions increased on average by at least 50\% across all subjects.
+Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics.
+On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%).
+The perfusion of parenchymal regions increased on average by 80\% across all three subjects.
 
@@
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
-Each row of charts depicts average vessel caliber, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
+Each row of charts depicts average vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
     }
@@
 Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals.
-A lone study using LDF found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
-However, because large blood vessels were avoided, the LDF likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI.
-The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by LDF, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.
+A lone study using laser Doppler flowmetry found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
+However, because large blood vessels were avoided, the laser Doppler measurements likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI.
+The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.
 
@@
 
-While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj, Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}.
+While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}.
 Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a range of flow rates \cite{Parthasarathy:2008el}.
@@
 The effects of isoflurane fundamentally undermine the imaging of cortical hemodynamics in the normal physiological state.
-Blood flow imaging techniques such as LSCI, LDF, and fMRI require greater sensitivity because of the suppression of the hemodynamic response \cite{Takuwa:2012ee} and measure a delayed neurovascular coupling \cite{Pisauro:2013cx}.
+Blood flow imaging techniques such as LSCI, laser Doppler flowmetry, and fMRI require greater sensitivity because of the suppression of the hemodynamic response \cite{Takuwa:2012ee} and measure a delayed neurovascular coupling \cite{Pisauro:2013cx}.
 Anatomical imaging with two-photon microscopy only captures heavily-dilated vasculature unrepresentative of the awake resting state \cite{Lyons:2016bd}.
@@
 Previous work has found that it can impair synaptic plasticity in the basolateral amygdala \cite{Long:2016ri} and cause persistent motor deficits via structural changes to the corpus callosum \cite{Bajwa:2018ri}.
-The one day interval between imaging sessions may not have been sufficient to avoid these effects despite only 20 minutes of isoflurane exposure.
+The one day interval between imaging sessions may not have been sufficient to completely avoid these effects despite only 20 minutes of isoflurane exposure.
 Because the experiment imaged the induction of general anesthesia from the awake state, tracheal intubation for mechanical ventilation was not an option.
@@
 Even with the head fully restrained, walking and grooming both cause subtle brain movements that manifest as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:acute}c.
-While these fluctuations may characterize real hemodynamic responses, it is difficult to isolate them from systemic animal motion.
+While these fluctuations may characterize real hemodynamic responses, it is difficult to isolate them from broader animal motion.
 A simple solution might be the addition of an external sensor to the treadmill \cite{Dombeck:2007gr} to exclude timepoints when the animal is actively moving.
-However, a more refined awake imaging system that minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI or other dynamic light scattering imaging techniques.
+However, a more refined awake imaging system that further minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI.
 
@@
 C.T.S.
-constructed the imaging system, conceived the experiments, acquired the data, analyzed the results, and wrote the manuscript.
+and L.M.R.
+constructed the imaging system, conceived the experiments, and acquired the data.
+C.T.S analyzed the results and wrote the manuscript.
 F.H.
@@
 His research focuses on the continued development and clinical translation of the laser speckle contrast imaging technique.
+
+\vspace{2ex}\noindent\textbf{Lisa M.
+Richards} received her PhD in biomedical engineering from the University of Texas at Austin in 2015.
+Currently, she is a Biomedical Systems Engineer at Seno Medical Instruments.
 

### 2020-06-10 article.tex
Added funding sources
Remove C. X. as author

@@
 \author[b]{Fei He}
-\author[b,c]{Chong Xie}
 \author[b,c]{Lan Luan}
@@
 performed the animal surgeries.
-C.X., L.L., and A.K.D.
+L.L.
+and A.K.D.
 supervised the project.
@@
 \acknowledgments
-This study was supported by the National Institutes of Health...
+This study was supported by the National Institutes of Health (Nos. EB011556 and NS108484).
 
@@
 
-\vspace{2ex}\noindent\textbf{Chong Xie} is an Associate Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative.
-His research focuses on the development of advanced nanoelectronic devices for probing and manipulating neural systems.
-
 \vspace{2ex}\noindent\textbf{Lan Luan} is an Assistant Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative.

### 2020-06-10 cover_letter.tex
Initial draft of cover letter

\documentclass[12pt,stdletter,orderfromtodate,dateleft,sigleft]{newlfm}
\usepackage[hidelinks]{hyperref}

\topmarginsize{0in}
\topmarginskip{0in}
\headermarginsize{0in}
\headermarginskip{0in}

\leftmarginsize{1in}
\rightmarginsize{1in}

\newlfmP{addrfromskipbefore=0pt}
\newlfmP{addrfromskipafter=0pt}

\newlfmP{sigskipbefore=10pt}
\newlfmP{sigsize=40pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{Colin Sullender, Ph.D.}
\addrfrom{%
    Colin Sullender\\
    The University of Texas at Austin\\
    Department of Biomedical Engineering\\
    107 W. Dean Keeton Street, Stop C0800\\
    Austin, TX, 78712, USA
}

\dateset{\today}

\greetto{Dear Dr. Boas,}

\closeline{Sincerely,}

\begin{document}
\begin{newlfm}

We wish to submit a new manuscript entitled ''Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging'' for consideration by \emph{Neurophotonics}. We confirm that this work is original and has not been published elsewhere nor is it currently under consideration in another journal.

In this paper, we present cerebral blood flow measurements in awake mice during the induction of general anesthesia with isoflurane. We utilize multi-exposure speckle imaging (MESI) to highlight the large anatomical changes caused by the vasodilatory inhalant. We also characterize the impact of the anesthesia on cortical hemodynamics across multiple subjects and imaging sessions.

This work is significant because it provides a unique insight into the acute effects of general anesthesia. Existing studies have largely focused on before and after point measurements of cortical hemodynamics whereas we present wide-field imagery during the induction itself. These results provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.

Please address all correspondence to Dr. Andrew Dunn at \href{mailto:adunn@utexas.edu}{\underline{adunn@utexas.edu}}.

Thank you for your consideration.

\end{newlfm}
\end{document}

### 2020-06-15 article.tex
Further revisions

@@
 There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics.
-Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
-Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
+Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
+Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
 Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
@@
 MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle.
-The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm.
-Fifteen camera exposures ranging between 50 $\mu$s and 80 ms {Parthasarathy:2008el, Atchia:2013ep, Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
+The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the modulated laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm.
+Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
 The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
-The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.
+The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.
 
@@
 Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}.
-Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}.
+Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event per photon \cite{Kazmi:2015du}.
 This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
@@
 
-Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
+Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical $O_2$ vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
 Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.).
@@
 After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function.
-After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
+After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
 The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames.
@@
 erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel.
-The vascular flux was then computed by scaling MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}.
+The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}.
 Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.
@@
         \label{fig:system_image}
-        (a) MESI system schematic with 2x magnification: L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
+        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
 (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).

### 2020-06-15 cover_letter.tex
Further revisions

@@
 We utilize multi-exposure speckle imaging (MESI) to highlight the large anatomical changes caused by the vasodilatory inhalant.
-We also characterize the impact of the anesthesia on cortical hemodynamics across multiple subjects and imaging sessions.
+We also characterize the impact of anesthesia on cortical hemodynamics across multiple subjects and imaging sessions.
 
 This work is significant because it provides a unique insight into the acute effects of general anesthesia.
-Existing studies have largely focused on before and after point measurements of cortical hemodynamics whereas we present wide-field imagery during the induction itself.
+Existing studies have largely focused on discrete measurements before and after the induction of anesthesia whereas we present wide-field imagery during the induction itself.
 These results provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.

### 2020-06-16 article.tex
Implemented edits from L. L.

@@
 There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics.
-Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
+Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
 Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
 Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
-To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
+However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
 
@@
 
-The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
+The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a $7\times7$-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
 %
@@
 This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
-This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
+This paper uses the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
 
@@
 The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging.
-They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.
+They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear treadmill awake imaging system \cite{He:2020}.
 
@@
 Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia.
-After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function.
+After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject.
 After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
@@
 
-The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1.
+The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to anesthetized state.
 The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
-Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
+Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
 These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.
@@
 The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b.
-The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure.
+The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure.
 This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c).
@@
 Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd).
+Calculated using 50 MESI frames acquired immediately before and after the continuous imaging session.
     }
@@
 \acknowledgments
-This study was supported by the National Institutes of Health (Nos. EB011556 and NS108484).
+This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, and NS109361).
 

### 2020-06-17 article.tex
Style edits

@@
 % Include a list of up to six keywords after the abstract
-\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, awake imaging, anesthesia}
+\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, awake imaging, anesthesia, isoflurane, cerebral blood flow}
 
 % Include email contact information for corresponding author
-{\noindent \footnotesize\textbf{*}Andrew K. Dunn,  \linkable{adunn@utexas.edu} }
+{\noindent \footnotesize\textbf{*}Andrew K. Dunn, \linkable{adunn@utexas.edu}}
 
@@
 MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle.
-The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the modulated laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm.
+The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the modulated laser pulses with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm.
 Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
@@
 
-The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a $7\times7$-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
+The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7$\times$7-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
 %

### 2020-06-17 article.tex
Implemented edits from F. H.

@@
 The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates.
-A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
-A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
-Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull.
-A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure.
-A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements.
+A circular region of the skull (4 mm diameter) over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
+The dura mater was also removed.
+A 4 mm round \#1.5 cover glass (World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
+Gentle pressure was applied to the cover glass while Kwik-Sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull.
+A layer of Vetbond tissue adhesive (3M) was applied over the Kwik-Sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure.
+C\&B Metabond (Parkell, Inc.) was then used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements.
 The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging.
@@
         \label{fig:system_image}
-        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
+        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
 (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
@@
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
-Each row of charts depicts average vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
+Each row of charts depicts vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states averaged across three different imaging sessions for each animal (mean $\pm$ sd).
     }

### 2020-06-19 article.tex
More revisions

@@
 We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions.
-Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchymal perfusion.
+Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchyma perfusion.
 These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
@@
 Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
-Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
+Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
 However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
@@
 
-The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to anesthetized state.
+The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state.
 The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
@@
         \label{fig:system_image}
-        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
-(b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
+        (a) MESI system schematic with 2$\times$ magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
+(b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
     }
@@
 
-The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session.
+The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session.
 The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b.
@@
 The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size.
-Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
+Repeated measurements in the subject (Figs.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to the isoflurane anesthesia.
 
@@
         \label{fig:acute}
-        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis.
-Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
+        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 1 mm).
+Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
 Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session.
@@
 The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
-Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd).
-Calculated using 50 MESI frames acquired immediately before and after the continuous imaging session.
+Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal across four imaging sessions (mean $\pm$ sd).
     }
@@
 The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}.
-Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each.
+Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states across three separate imaging sessions lasting 30 minutes each.
 Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics.
@@
         \label{fig:summary}
-        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis.
-Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm).
-Each row of charts depicts vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states averaged across three different imaging sessions for each animal (mean $\pm$ sd).
+        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis (Scale bar = 1 mm).
+Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
+Each row of charts depicts vessel diameter, vascular flux, and parenchyma tissue perfusion during awake and anesthetized states averaged across three separate imaging sessions for each animal (mean $\pm$ sd).
     }

### 2020-06-25 cover_letter.tex
Swap to just using {letter} template for cover letter
Fixed quotation marks around article title

@@
-\documentclass[12pt,stdletter,orderfromtodate,dateleft,sigleft]{newlfm}
+\documentclass[12pt]{letter}
+\usepackage[a4paper]{geometry}
 \usepackage[hidelinks]{hyperref}
 
-\topmarginsize{0in}
-\topmarginskip{0in}
-\headermarginsize{0in}
-\headermarginskip{0in}
-
-\leftmarginsize{1in}
-\rightmarginsize{1in}
-
-\newlfmP{addrfromskipbefore=0pt}
-\newlfmP{addrfromskipafter=0pt}
-
-\newlfmP{sigskipbefore=10pt}
-\newlfmP{sigsize=40pt}
-
-\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
-
-\namefrom{Colin Sullender, Ph.D.}
-\addrfrom{%
+\name{Colin Sullender}
+\address{
     Colin Sullender\\
@@
 }
-
-\dateset{\today}
-
-\greetto{Dear Dr. Boas,}
-
-\closeline{Sincerely,}
+\signature{\vspace{50pt} Colin Sullender, Ph.D.}
+\longindentation=0pt
 
 \begin{document}
-\begin{newlfm}
+\begin{letter}{}
 
-We wish to submit a new manuscript entitled ''Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging'' for consideration by \emph{Neurophotonics}.
+\opening{Dear Dr. Boas,}
+
+We wish to submit a new manuscript entitled ``Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging'' for consideration by \emph{Neurophotonics}.
 We confirm that this work is original and has not been published elsewhere nor is it currently under consideration in another journal.
@@
 
-\end{newlfm}
+\closing{Sincerely,}
+
+\end{letter}
 \end{document}

### 2020-06-25 article.tex
Implemented edits from L. M. R.

@@
 Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
-However, to date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
+To our knowledge, no prior studies have directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
 
@@
 We highlight the large anatomical and physiological changes to cortical hemodynamics in response to isoflurane with wide-field imagery across multiple imaging sessions and animals.
-Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible.
+Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible for neuroscience studies.
 
@@
 MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle.
-The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the modulated laser pulses with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm.
+The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm.
+Camera exposures were temporally synchronized with the modulated laser pulses.
 Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
@@
 
-Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
-The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}).
+Cranial window implanted mice ($n = 3$, Subjects 2-4) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
+The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}).
 A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%).
@@
 
-An additional subject ($n = 1$) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
+An additional subject ($n = 1$, Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
 Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery.
-The timing of the anesthesia induction is identical to the protocol described above.
+The timing of the anesthesia induction was identical to the protocol described above with the awake and anesthetized states defined at $t = 0$ and $t = 120$ minutes, respectively.
 The four repeated imaging sessions for this subject were spaced at least one week apart to minimize any complications from extended anesthesia exposure.
@@
 In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery prior to fitting Eq.~(\ref{eq:mesi}).
-The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second.
+The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed).
 $ICT$ timecourses spanning the entire imaging session were also extracted from the fitted data from both vascular and parenchymal regions of interest.
 
-In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) was estimated using the 5 ms exposure speckle contrast frames.
+In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) were estimated using the 5 ms exposure speckle contrast frames.
 Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution.
@@
 
-The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state.
+The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state.
 The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
 Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
-These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.
+These large alterations to the vasculature complicated rigid image registration and precluded the generation of relative flow change imagery.
 
@@
         \label{fig:system_image}
-        (a) MESI system schematic with 2$\times$ magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
-(b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
+        (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$''$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
+(b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
     }
@@
 
-The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session.
+The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1.
 The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b.
@@
         \label{fig:acute}
-        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 1 mm).
+        (a) Awake speckle contrast image (5 ms) from Subject 1 overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 500 $\mu$m).
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
-Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session.
+Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over the extended two-hour imaging session.
 The vertical dashed line indicates the beginning of anesthesia induction.
 The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
-Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal across four imaging sessions (mean $\pm$ sd).
+Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in Subject 1 across four imaging sessions (mean $\pm$ sd).
+Statistics computed across 50 MESI frames acquired in each state.
     }
@@
 Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics.
-On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%).
+On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 2, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%).
 The perfusion of parenchymal regions increased on average by 80\% across all three subjects.
@@
         \label{fig:summary}
-        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis (Scale bar = 1 mm).
+        Awake speckle contrast images (5 ms) from Subjects 1-3 overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis (Scale bars = 500 $\mu$m).
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
-Each row of charts depicts vessel diameter, vascular flux, and parenchyma tissue perfusion during awake and anesthetized states averaged across three separate imaging sessions for each animal (mean $\pm$ sd).
+Each row of charts depicts vessel diameter, vascular flux, and parenchyma tissue perfusion during awake and anesthetized states averaged across three separate imaging sessions for each subject (mean $\pm$ sd).
+Statistics computed across each imaging session with uncertainty propagation from the 50 MESI frames acquired in each state.
     }
@@
 Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials.
-Even vessels that experienced only minimal vasodilation, such as R2 for Subject 1 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow.
+Even vessels that experienced only minimal vasodilation, such as R2 for Subject 2 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow.
 Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals.
-A lone study using laser Doppler flowmetry found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
+One study using laser Doppler flowmetry found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
 However, because large blood vessels were avoided, the laser Doppler measurements likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI.
-The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.
+The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so the results are not directly comparable \cite{Kazmi:2015du}.
 
@@
 While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}.
-Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a range of flow rates \cite{Parthasarathy:2008el}.
+Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a small range of flow rates \cite{Parthasarathy:2008el}.
 Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the visible surface vasculature.
@@
 A simple solution might be the addition of an external sensor to the treadmill \cite{Dombeck:2007gr} to exclude timepoints when the animal is actively moving.
-However, a more refined awake imaging system that further minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI.
+However, a more refined awake imaging system that further minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI or MESI.
 
@@
 These increases in vessel size and blood flow were repeatable across multiple imaging sessions in the same subjects.
-This study also demonstrated that the MESI technique can be readily used for chronic awake imaging and allows for direct day-to-day and animal-to-animal comparisons of blood flow.
+This study also demonstrated that the MESI technique can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
 These results provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.
@@
 \acknowledgments
-This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, and NS109361).
+This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, NS109361, and T32EB007507).
 
@@
 Richards} received her PhD in biomedical engineering from the University of Texas at Austin in 2015.
-Currently, she is a Biomedical Systems Engineer at Seno Medical Instruments.
+Currently, she is a Senior Biomedical Systems Engineer at Seno Medical Instruments.
 

### 2020-06-26 article.tex
Further revisions

@@
 \usepackage{tocloft}
+\usepackage[version=4]{mhchem}
 
@@
         \beta(1 - \rho)^2 +
-        \nu_{ne} +
         \nu_{noise}
@@
 Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event per photon \cite{Kazmi:2015du}.
-This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
+This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of ``vascular flux'' that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
 This paper uses the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
@@
 
-Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical $O_2$ vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
+Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical \ce{O2} vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation.
 Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.).
@@
 The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates.
-A circular region of the skull (4 mm diameter) over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
-The dura mater was also removed.
+A circular region (4 mm diameter) of the skull including the dura mater over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
 A 4 mm round \#1.5 cover glass (World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
@@
 
-An additional subject ($n = 1$, Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
+An additional animal (Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
 Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery.
@@
 The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%.
-The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes.
+The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes.
 The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size.
@@
 Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in Subject 1 across four imaging sessions (mean $\pm$ sd).
-Statistics computed across 50 MESI frames acquired in each state.
+Statistics computed across the 50 MESI frames acquired in each state.
     }
@@
 
-The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}.
+The repeatability of these measurements were further demonstrated across Subjects 2-4 as shown in Fig.~\ref{fig:summary}.
 Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states across three separate imaging sessions lasting 30 minutes each.
@@
 Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials.
-Even vessels that experienced only minimal vasodilation, such as R2 for Subject 2 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow.
+Even vessels that experienced only minimal vasodilation, such as R2 for Subject 2 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow as measured with MESI.
 Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals.
@@
 
-Within the parenchyma, perfusion increased on average by 92 $\pm$ 35\% across all trials after only 20 minutes of isoflurane exposure.
+Within the parenchyma, perfusion increased on average by 92 $\pm$ 35\% across all trials after isoflurane exposure.
 The reduced variability compared to the vascular measurements is likely a byproduct of the more homogenous structure of the unresolvable capillaries within the parenchyma.

### 2020-06-26 article.tex
Added line numbering
Stripped figure list and author biographies

@@
 
-% ----------------------------------------------------------------------------------------
-% AUTHOR BIOGRAPHIES
-% ----------------------------------------------------------------------------------------
-\vspace{1ex}
-\vspace{2ex}\noindent\textbf{Colin T.
-Sullender} received his PhD in biomedical engineering from the University of Texas at Austin in 2018.
-Currently, he is a postdoctoral research fellow working with Dr.
-Andrew Dunn in the Functional Optical Imaging Laboratory (FOIL) at the University of Texas.
-His research focuses on the continued development and clinical translation of the laser speckle contrast imaging technique.
-
-\vspace{2ex}\noindent\textbf{Lisa M.
-Richards} received her PhD in biomedical engineering from the University of Texas at Austin in 2015.
-Currently, she is a Senior Biomedical Systems Engineer at Seno Medical Instruments.
-
-\vspace{2ex}\noindent\textbf{Fei He} received his PhD in optical engineering from the Chinese Academy of Sciences.
-Currently, he is a postdoctoral research fellow working with Dr.
-Lan Luan in the Luan Laboratory of Integrative Neural Interface at Rice University.
-
-\vspace{2ex}\noindent\textbf{Lan Luan} is an Assistant Professor in the Department of Electrical and Computer Engineering at Rice University and a member of the Rice Neuroengineering Initiative.
-Her research focuses on the development of multimodal neural interfaces that combine electrical, optical, and other technologies to monitor and manipulate brain activity.
-
-\vspace{2ex}\noindent\textbf{Andrew K.
-Dunn} is the Donald J.
-Douglass Centennial Professor of Engineering in the Department of Biomedical Engineering at the University of Texas at Austin and the Director of the Center for Emerging Imaging Technologies.
-His research focuses on the development of innovative optical imaging techniques for studying the brain.
-
-% ----------------------------------------------------------------------------------------
-% FIGURE AND TABLE LISTS
-% ----------------------------------------------------------------------------------------
-\listoffigures
-
 \end{spacing}

### 2020-06-30 article.tex
Transitioned to structured abstract

--- 2020-06-26 article.tex
@@
 \newunicodechar{β}{$\beta$}
+
+% Structured abstract section formatting
+\newcommand{\abstractsection}[1]{
+  \par\addvspace{.5\baselineskip}
+  \noindent\textbf{#1: }\ignorespaces
+}
 
@@
 \begin{abstract}
+
+\abstractsection{Significance}
 Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology.
-In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI).
-We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions.
+The majority of work examining the impact of anesthesia on cerebral blood flow (CBF) has been limited to before and after measurements with limited spatial resolution.
+
+\abstractsection{Aim}
+Characterize the effects of isoflurane on CBF during the induction of general anesthesia using multi-exposure speckle imaging (MESI).
+
+\abstractsection{Approach}
+Head-restrained awake mice were continuously imaged with MESI as general anesthesia was induced with isoflurane.
+MESI was used to estimate changes in cortical hemodynamics including vessel size, vascular flow, and parenchyma perfusion across multiple imaging sessions and animals.
+
+\abstractsection{Results}
+The large anatomical changes caused by isoflurane are depicted with wide-field imagery and video highlighting the induction of anesthesia.
 Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchyma perfusion.
-These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
+
+\abstractsection{Conclusions}
+The large alterations caused by isoflurane anesthesia to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
+
 \end{abstract}

### 2021-07-14 article.tex
Initial revision for submission to Journal of Neuroscience Methods
- Focus more on acute dynamics of anesthesia rather than before/after measurements
- Swapped back to original MESI equation (Parthasarathy, 2008)
- Added analysis of isoflurane dynamics (flow rise time)
- Transitioned to Elsevier style

--- 2020-06-26 article.tex
@@
-\documentclass[12pt]{spieman}
+\documentclass[review]{elsarticle}
+
 \usepackage{amsmath,amsfonts,amssymb}
 \usepackage{graphicx}
+\usepackage{siunitx}
 \usepackage{setspace}
@@
 
-% ---------------------------------------------------------------------------------------
-% BEGIN TITLE AND AUTHORS
-% ---------------------------------------------------------------------------------------
-\title{Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging}
-
-\author[a]{Colin T. Sullender}
-\author[a]{Lisa M. Richards}
-\author[b]{Fei He}
-\author[b,c]{Lan Luan}
-\author[a,*]{Andrew K. Dunn}
-\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
-\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
-\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
+% Structured abstract section formatting
+\newcommand{\abstractsection}[1]{
+  \par\addvspace{.5\baselineskip}
+  \noindent\textbf{#1: }\ignorespaces
+}
 
@@
 % ----------------------------------------------------------------------------------------
-\renewcommand{\cftdotsep}{\cftnodots}
-\cftpagenumbersoff{figure}
-\cftpagenumbersoff{table} 
 \begin{document}
-\maketitle
+
+\begin{frontmatter}
+
+\journal{Journal of Neuroscience Methods}
+
+\title{Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by laser speckle contrast imaging}
+
+% Authors
+\author[a]{Colin T. Sullender}
+
+\author[a]{Lisa M. Richards}
+
+\author[b]{Fei He}
+
+\author[b,c]{Lan Luan}
+
+\author[a]{Andrew K. Dunn\corref{corr_auth}}
+\ead{adunn@utexas.edu}
+\cortext[corr_auth]{Corresponding Author}
+
+% Affiliations
+\affiliation[a]{
+    organization={Department of Biomedical Engineering, University of Texas at Austin},
+    addressline={107 W. Dean Keeton Street Stop C0800},
+    city={Austin, TX},
+    postcode={78712},
+    country={United States}
+}
+
+\affiliation[b]{
+    organization={Department of Electrical and Computer Engineering, Rice University},
+    addressline={6100 Main Street},
+    city={Houston, TX},
+    postcode={77005},
+    country={United States}
+}
+
+\affiliation[c]{
+    organization={Department of Bioengineering, Rice University},
+    addressline={6100 Main Street},
+    city={Houston, TX},
+    postcode={77005},
+    country={United States}
+}
 
@@
 \begin{abstract}
+
+\abstractsection{Background}
 Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology.
-In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI).
-We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions.
-Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchyma perfusion.
-These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
+The majority of work examining the impact of anesthesia on cerebral blood flow (CBF) has been limited to before and after measurements with limited spatial resolution.
+
+\abstractsection{New Method}
+We used multi-exposure speckle imaging (MESI), an advanced form of laser speckle contrast imaging (LSCI), to characterize the dynamics of isoflurane anesthesia induction on cerebral vasculature and blood flow in the mouse brain.
+
+\abstractsection{Results}
+The large anatomical changes caused by isoflurane are depicted with wide-field imagery and video highlighting the induction of anesthesia.
+Compared to the awake state, we measured, on average, a 14.1\% increase in surface vessel diameter accompanied by a 96.0\% increase in vascular flux and 84.7\% increase in parenchyma tissue perfusion.
+We also examined the dynamics of anesthesia induction and found that blood flow increased faster in arterioles than in venules or parenchyma regions.
+
+\abstractsection{Comparison with Existing Methods}
+MESI offers robust hemodynamic measurements across large fields-of-view and high temporal resolutions sufficient for continuous visualization of cerebrovascular events.
+
+\abstractsection{Conclusion}
+The large alterations caused by isoflurane anesthesia to the cortical vasculature and CBF are readily characterized using MESI.
+These changes are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
+
 \end{abstract}
@@
 % Include a list of up to six keywords after the abstract
-\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, awake imaging, anesthesia, isoflurane, cerebral blood flow}
+\begin{keyword}
+    laser speckle contrast imaging \sep
+    multi-exposure speckle imaging \sep
+    awake imaging \sep
+    anesthesia \sep
+    hemodynamics \sep
+    cerebral blood flow
+\end{keyword}
 
-% Include email contact information for corresponding author
-{\noindent \footnotesize\textbf{*}Andrew K. Dunn, \linkable{adunn@utexas.edu}}
-
-\begin{spacing}{2}   % use double spacing for rest of manuscript
+\end{frontmatter}
 
@@
 \section{Introduction}
-\label{sect:introduction}
 
@@
 Volatile inhalation anesthetics, such as the halogenated ether isoflurane \cite{Eger:1981ia}, are commonly utilized to immobilize animals during imaging while allowing for fine control over the depth of anesthesia and consciousness.
-However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Strebel:1995uh,Iida:1998th}.
+However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Iida:1998th}.
 Isoflurane also conveys potential neuroprotective effects that reduce and delay the severity of cerebral ischemia \cite{Kitano:2007ia,Kawaguchi:2000id,Sakai:2007wc,Li:2013ip,Lu:2017bo}.
@@
 There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics.
-Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
+Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}.
 Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}.
 Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}.
-To our knowledge, no prior studies have directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.
+To our knowledge, no prior studies have directly imaged the induction of general anesthesia and its acute effects upon the cerebral vasculature.
 
@@
 The MESI technique \cite{Parthasarathy:2008el} provides a more robust estimate of large changes in flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo} and enables the chronic tracking of CBF \cite{Kazmi:2013hp}.
-We highlight the large anatomical and physiological changes to cortical hemodynamics in response to isoflurane with wide-field imagery across multiple imaging sessions and animals.
+We examine the dynamics of the large anatomical and physiological changes to cortical vasculature in response to isoflurane with wide-field imagery across multiple imaging sessions and animals.
 Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible for neuroscience studies.
@@
 % ----------------------------------------------------------------------------------------
-\section{Methods}
-\label{sect:methods}
+\section{Materials and Methods}
 
 \subsection{Multi-Exposure Speckle Imaging (MESI)}
-A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a.
+A schematic of the imaging system is presented in Fig.~\ref{fig:system}a.
 MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle.
@@
         4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
-        \beta(1 - \rho)^2 +
         \nu_{noise}
@@
 \noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu_{noise}$ represents exposure-independent instrument noise and nonergodic variances.
-Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:2005} using a custom program written in C.
+Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in C.
 
@@
 
-Cranial window implanted mice ($n = 3$, Subjects 2-4) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
+Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
 The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}).
@@
 Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia.
-After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject.
-After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
-The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames.
+After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject.
+After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
+The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames.
 The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage.
@@
 
-An additional animal (Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
+One animal (Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics.
 Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery.
@@
 
+All data processing was performed using MATLAB (R2021a, MathWorks, Inc.).
 While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts.
-The induction of general anesthesia also causes a major change in posture that can result in lateral displacements of the brain relative to the skull.
-In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery prior to fitting Eq.~(\ref{eq:mesi}).
+The induction of general anesthesia also causes major changes in posture that can result in lateral displacements of the brain relative to the skull.
+In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the baseline awake imagery prior to fitting Eq.~(\ref{eq:mesi}).
 The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed).
-$ICT$ timecourses spanning the entire imaging session were also extracted from the fitted data from both vascular and parenchymal regions of interest.
+$ICT$ timecourses spanning the entire imaging session were then extracted from the aligned data from both vascular and parenchymal regions of interest (ROIs).
 
-In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) were estimated using the 5 ms exposure speckle contrast frames.
-Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution.
+\subsubsection{Calculating Vascular Flux}
+In order to calculate the vascular flux \cite{Kazmi:2015du}, the diameter of vessels ($d_{vessel}$) were estimated using the 5 ms exposure speckle contrast frames.
+Cross-sectional profiles were extracted across each vessel of interest at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution over time.
 Because LSCI is most sensitive to moving scatterers, i.e.
 erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel.
-The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}.
-Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.
+The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint (arbitrary units).
+The percent change in vessel diameter and vascular flux were calculated using the average of the entire awake state for the baseline.
+
+\subsubsection{Calculating Blood Flow Rise Time}
+To examine the dynamics of isoflurane-induced flow changes, the rise time in measured blood flow was calculated.
+Rise time was defined as the time elapsed following the start of anesthesia for $ICT$ values to increase by 50\% relative to the awake baseline.
+A spatially-resolved blood flow rise time map was generated for Subject 1 by performing this calculation pixel-wise across the entire field-of-view.
+Analogous rise time calculations were performed on the vascular flux and parenchymal tissue perfusion metrics across all subjects and imaging sessions using the previously extracted ROI timecourses.
+
+\subsubsection{Statistical Analysis}
+All statistical analyses were performed using MATLAB (R2021a, MathWorks, Inc.).
+The differences between arteriole, venule, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons.
+$p \leq 0.05$ was considered statistically significant.
 
@@
 \section{Results}
-\label{sect:results}
 
-The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state.
-The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}.
+The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system}b and Video 1, which highlights the transition from the awake to the anesthetized state.
+The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane.
 Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
@@
 \begin{figure}
-    \begin{center}
-        \begin{tabular}{c}
-            \includegraphics[width=6.25in]{Figure1.pdf}
-        \end{tabular}
-    \end{center}
+    \includegraphics[width=\textwidth]{Figure1.pdf}
     \caption {
-        \label{fig:system_image}
-        (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$''$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
-(b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
+        (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$"$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
+(b) Single exposure LSCI (5 ms) and MESI inverse correlation time ($ICT$) during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG-4, 35.8 MB).
     }
+    \label{fig:system}
 \end{figure}
 
-The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1.
-The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b.
-The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure.
-This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c).
-The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%.
-The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes.
+The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:timecourse}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1.
+The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:timecourse}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:timecourse}b.
+The width of the two vessels remained steady throughout the entirety of the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure.
+This vasodilation was also accompanied by an increase in blood flow as measured by the percent change in vascular flux and parenchymal tissue perfusion as shown in Fig.~\ref{fig:timecourse}c.
+The vascular flux in R1 and R2 increased by 270\% and 144\%, respectively, while the tissue perfusion in R3 grew by 141\%.
+The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia be reduced to 1.5\% isoflurane for several minutes.
 The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size.
-Repeated measurements in the subject (Figs.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to the isoflurane anesthesia.
+Repeated measurements in the subject (Figs.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
 
@@
 \begin{figure}
-    \begin{center}
-        \begin{tabular}{c}
-            \includegraphics[width=6.25in]{Figure2.pdf}
-        \end{tabular}
-    \end{center}
+    \includegraphics[width=\textwidth]{Figure2.pdf}
     \caption {
-        \label{fig:acute}
         (a) Awake speckle contrast image (5 ms) from Subject 1 overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 500 $\mu$m).
 Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
-Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over the extended two-hour imaging session.
+Timecourses of (b) vessel diameter and (c) percent change in blood flow within the regions over the extended two-hour imaging session.
 The vertical dashed line indicates the beginning of anesthesia induction.
-The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
+The percent change in vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline.
 Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in Subject 1 across four imaging sessions (mean $\pm$ sd).
@@
     }
+    \label{fig:timecourse}
 \end{figure}
 
-The repeatability of these measurements were further demonstrated across Subjects 2-4 as shown in Fig.~\ref{fig:summary}.
-Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states across three separate imaging sessions lasting 30 minutes each.
-Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics.
-On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 2, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%).
-The perfusion of parenchymal regions increased on average by 80\% across all three subjects.
+The percent changes in vessel diameter and blood flow between the awake and anesthetized states were aggregated across all subjects and imaging sessions as shown in Fig.~\ref{fig:aggregated}.
+The anesthetized measurements for Subject 1, which underwent the extending imaging sessions, were taken at $t \approx 80$ minutes to match the timing of the other subjects (20 minutes after the start of anesthesia).
+A total of 108 measurements were included in the analysis (33 arteriole, 29 venule, 46 parenchyma).
+Similar to the results seen in Fig.~\ref{fig:timecourse}, the vasodilatory effects of isoflurane induced large changes in the cortical hemodynamics.
+On average, vessel width increased by 14.1\%, with arterioles increasing by 15.0\% and venules increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
+There was no significant difference in the percent change in width between arterioles and venules ($p = 0.61$).
+Vascular flux increased, on average, by 96.0\%, with arterioles increasing by 81.7\% and venules increasing by 112.2\% (Fig.~\ref{fig:aggregated}b).
+Parenchymal tissue perfusion increased by 84.7\%.
+While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arterioles, venules, and parenchyma were all non-significant ($p > 0.05$).
 
-% Figure 3 - Awake to Anesthetized Results Summary
+% Figure 3 - Aggregated Awake to Anesthetized Results
 \begin{figure}
-    \begin{center}
-        \begin{tabular}{c}
-            \includegraphics[width=6.25in]{Figure3.pdf}
-        \end{tabular}
-    \end{center}
+    \includegraphics[width=\textwidth]{Figure3.pdf}
     \caption {
-        \label{fig:summary}
-        Awake speckle contrast images (5 ms) from Subjects 1-3 overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis (Scale bars = 500 $\mu$m).
-Dashed lines indicate the cross-sectional profiles used to calculate vessel width.
-Each row of charts depicts vessel diameter, vascular flux, and parenchyma tissue perfusion during awake and anesthetized states averaged across three separate imaging sessions for each subject (mean $\pm$ sd).
-Statistics computed across each imaging session with uncertainty propagation from the 50 MESI frames acquired in each state.
+        (a) Percent change in vessel diameter for arterioles and venules between awake and anesthetized states ($p > 0.05$).
+(b) Percent change in arteriolar and venous vascular flux and parenchymal tissue perfusion between awake and anesthetized states ($p > 0.05$).
+Measurements in both charts aggregated across all subjects and all imaging sessions.
     }
+    \label{fig:aggregated}
+\end{figure}
+
+The dynamics of the isoflurane-induced flow changes in Subject 1 can be seen in the blood flow rise time map in Fig.~\ref{fig:risetime}a.
+$ICT$ values across the entire field-of-view increased by at least 50\% in just over one minute following the start of anesthesia.
+The vasculature, including both arterioles and venules, appears to change flow faster than the parenchyma.
+However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b), arterioles have significantly faster rise times ($40.5$ seconds) compared to venules ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma ($46.1$ seconds, $p = 0.006$).
+Parenchymal regions also have significantly faster rise times than venules ($p = 0.043$).
+
+% Figure 4 - Hemodynamic Rise Time
+\begin{figure}
+    \includegraphics[width=\textwidth]{Figure4.pdf}
+    \caption {
+        (a) Blood flow rise time map depicting the time elapsed following the start of anesthesia for the inverse correlation time ($ICT$) to increase by 50\% relative to awake baseline in Subject 1 (Scale bar = 1 mm).
+(b) Time for arteriolar and venous vascular flux and parenchymal tissue perfusion to increase by 50\% relative to the awake baseline (***$p = \num{3.7e-6}$, **$p = 0.006$, *$p = 0.043$).
+Measurements aggregated across all subjects and all imaging sessions.
+    }
+    \label{fig:risetime}
 \end{figure}
@@
 \section{Discussion}
-\label{sect:discussion}
 
 The systemic effects of isoflurane undermine the reliability of neurophysiological and behavioral studies because anesthesia is a fundamentally unnatural physiological state \cite{Gao:2017tw}.
-Imaging blood flow on the cortical surface with MESI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
-On average, the vasodilation caused by isoflurane increased vessel diameter by 18 $\pm$ 13\% across all trials with large vessel-to-vessel variation but small day-to-day variation (Fig.~\ref{fig:summary}).
+Imaging blood flow on the cortical surface with LSCI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
+On average, the vasodilation caused by isoflurane increased vessel diameter by 14.1\% across all trials, with arterioles increasing by 15.0\% and venules increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
 Direct microscope measurements in fentanyl- and nitrous oxide-anesthetized rats documented a 17\% increase in arteriolar diameter and 6\% increase in venule diameter after the topical application of isoflurane \cite{Koenig:1994rn}.
@@
 Both studies found that isoflurane dilated arterioles in a concentration-dependent manner.
+More recent measurements in mice using optical coherence tomography (OCT) angiography found that isoflurane increased artery diameter by 12-55\% and vein diameter by 14-22\%, depending on vessel branch order \cite{Rakymzhan.2021}.
 
-Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials.
-Even vessels that experienced only minimal vasodilation, such as R2 for Subject 2 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow as measured with MESI.
+Much larger changes were measured in surface vessel blood flow, with vascular flux increasing on average by 96.0\% across all trials (Fig.~\ref{fig:aggregated}b).
+This suggests that increases in blood flow velocity rather than vasodilation are largely responsible for the measured change in flow.
 Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals.
 One study using laser Doppler flowmetry found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}.
-However, because large blood vessels were avoided, the laser Doppler measurements likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI.
+However, because large blood vessels were avoided, the laser Doppler measurements only sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged in this study.
 The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so the results are not directly comparable \cite{Kazmi:2015du}.
+Another more recent study using Doppler OCT measured a 55\% increase in total (volumetric) blood flow in mice under isoflurane \cite{Rakymzhan.2021}.
+Unlike the results presented above, this change was largely driven by vasodilation rather than an increase in blood flow velocity.
 
-Within the parenchyma, perfusion increased on average by 92 $\pm$ 35\% across all trials after isoflurane exposure.
-The reduced variability compared to the vascular measurements is likely a byproduct of the more homogenous structure of the unresolvable capillaries within the parenchyma.
+Within the parenchyma, tissue perfusion increased on average by 84.7\% across all trials after isoflurane exposure (Fig.~\ref{fig:aggregated}b).
+The narrower distribution of values compared to the vascular measurements is likely a byproduct of the more homogenous structure of the unresolvable capillaries within the parenchyma.
 fMRI measurements in isoflurane-anesthetized rats have reported $\sim$50\% increases in global CBF with the cerebral cortex experiencing the smallest regional increase (20\%) compared to the awake state \cite{Sicard:2003dj}.
-However, these numbers are not directly comparable because fMRI samples a much larger volume of the brain than MESI, which has both a smaller field of view and only penetrates several hundred microns into the cortex.
+However, these numbers are not directly comparable because fMRI samples a much larger volume of the brain than LSCI, which has both a smaller field-of-view and only penetrates several hundred microns into the cortex.
 
@@
 Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a small range of flow rates \cite{Parthasarathy:2008el}.
-Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the visible surface vasculature.
-Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:acute}c would have measured only a 140\% increase in the large vessel instead of 267\%.
-The repeatability of the day-to-day measurements further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
+Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the surface vasculature.
+Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%.
+The repeatability of the day-to-day measurements shown in Figs.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
+
+The generation of the blood flow rise time map (Fig.~\ref{fig:risetime}a) highlights the continuous wide-field imaging capabilities of MESI.
+Other blood flow imaging techniques such as laser Doppler flowmetry, OCT, or fMRI would be restricted by either spatial or temporal resolution from performing such an analysis.
+The spatial heterogeneity in the mapping reveals differing dynamics between the vasculature and parenchyma as confirmed with the aggregated ROI analysis in Fig.~\ref{fig:risetime}b.
+While image registration was used to spatially align the $ICT$ frames, the isoflurane-induced vasodilation complicated this process and resulted in imperfect alignment.
+The effects of this are most pronounced along the periphery of vasculature where the vasodilatory changes were the most prominent.
 
@@
 Anatomical imaging with two-photon microscopy only captures heavily-dilated vasculature unrepresentative of the awake resting state \cite{Lyons:2016bd}.
-The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:acute}b.
+The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:timecourse}b.
 This may result in extended imaging sessions documenting disparate anatomies and physiologies between the beginning and conclusion of an experiment.
@@
 While image registration can help maintain the spatial alignment of data across an experiment, it is unable to decouple the effects of animal motion from the underlying blood flow.
-Even with the head fully restrained, walking and grooming both cause subtle brain movements that manifest as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:acute}c.
-While these fluctuations may characterize real hemodynamic responses, it is difficult to isolate them from broader animal motion.
+Even with the head fully restrained, walking and grooming both cause subtle brain movements that manifest as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:timecourse}c.
+While these fluctuations may represent real hemodynamic responses, it is difficult to isolate them from broader animal motion.
 A simple solution might be the addition of an external sensor to the treadmill \cite{Dombeck:2007gr} to exclude timepoints when the animal is actively moving.
@@
 \section{Conclusion}
-\label{sect:conclusion}
 
-We have used MESI to image CBF during the induction of general anesthesia with isoflurane in head-restrained mice.
-The vasodilatory effects of isoflurane caused large anatomical and physiological changes that were drastically different from the awake state.
-These increases in vessel size and blood flow were repeatable across multiple imaging sessions in the same subjects.
-This study also demonstrated that the MESI technique can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
+We have used MESI to continuously image CBF during the induction of general anesthesia with isoflurane in head-restrained mice.
+The vasodilatory effects of isoflurane caused rapid and large anatomical and physiological changes that were drastically different from the awake state.
+These increases in vessel size and blood flow were repeatable across multiple imaging sessions and subjects.
+This study also demonstrated that MESI can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
 These results provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.
@@
 % ----------------------------------------------------------------------------------------
-% BEGIN DISCLOSURES AND ACKNOWLEDGEMENTS
+% BEGIN ACKNOWLEDGEMENTS AND DISCLOSURES
 % ----------------------------------------------------------------------------------------
-\subsection*{Disclosures}
+
+\section*{Acknowledgements}
+This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, NS109361, and T32EB007507).
+
+\section*{Disclosures}
 A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.
 
-\subsection*{Author Contributions}
+\section*{Author Contributions}
 C.T.S.
@@
 
-\acknowledgments
-This study was supported by the National Institutes of Health (Nos. EB011556, HL140153, NS108484, NS109361, and T32EB007507).
-
 % ----------------------------------------------------------------------------------------
@@
 \bibliography{bibliography.bib}
-\bibliographystyle{spiejour} % SPIE bibliography style
-
-\end{spacing}
-\end{document}
+\bibliographystyle{elsarticle-num}
 
@@
 % ----------------------------------------------------------------------------------------
+\end{document}

### 2021-08-18 article.tex
Revisions

@@
 
-\title{Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by laser speckle contrast imaging}
+\title{Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by multi-exposure speckle imaging}
 
@@
 Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology.
-The majority of work examining the impact of anesthesia on cerebral blood flow (CBF) has been limited to before and after measurements with limited spatial resolution.
+The majority of work examining the impact of anesthesia on cerebral blood flow (CBF) has been restricted to before and after measurements with limited spatial resolution.
 
@@
 \abstractsection{Results}
-The large anatomical changes caused by isoflurane are depicted with wide-field imagery and video highlighting the induction of anesthesia.
-Compared to the awake state, we measured, on average, a 14.1\% increase in surface vessel diameter accompanied by a 96.0\% increase in vascular flux and 84.7\% increase in parenchyma tissue perfusion.
-We also examined the dynamics of anesthesia induction and found that blood flow increased faster in arterioles than in venules or parenchyma regions.
+The large anatomical changes caused by isoflurane are depicted with wide-field imagery and video highlighting the induction of general anesthesia.
+Within minutes of exposure, both vessel diameter and blood flow increased drastically compared to the awake state and remained elevated for the duration of imaging.
+An examination of the dynamics of anesthesia induction reveals that blood flow increased faster in arteries than in veins or parenchyma regions.
 
 \abstractsection{Comparison with Existing Methods}
-MESI offers robust hemodynamic measurements across large fields-of-view and high temporal resolutions sufficient for continuous visualization of cerebrovascular events.
+MESI offers robust hemodynamic measurements across large fields-of-view and high temporal resolutions sufficient for continuous visualization of cerebrovascular events featuring major changes in blood flow.
 
@@
 \begin{keyword}
+    multi-exposure speckle imaging \sep
     laser speckle contrast imaging \sep
-    multi-exposure speckle imaging \sep
     awake imaging \sep
@@
         4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
-        \nu_{noise}
+        \nu
         \right)^{1/2}
@@
 
-\noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu_{noise}$ represents exposure-independent instrument noise and nonergodic variances.
+\noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu$ represents exposure-independent instrument noise and nonergodic variances.
 Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in C.
@@
 This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of ``vascular flux'' that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}.
-This paper uses the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.
+This paper uses the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchyma perfusion measurements.
 
@@
 Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia.
-After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject.
+After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane.
 After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
@@
 In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the baseline awake imagery prior to fitting Eq.~(\ref{eq:mesi}).
-The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed).
+The resulting aligned $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed).
 $ICT$ timecourses spanning the entire imaging session were then extracted from the aligned data from both vascular and parenchymal regions of interest (ROIs).
@@
 erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel.
-The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint (arbitrary units).
+The vascular flux was then computed by scaling the $ICT$ by $d_{vessel}$ at each timepoint.
 The percent change in vessel diameter and vascular flux were calculated using the average of the entire awake state for the baseline.
@@
 To examine the dynamics of isoflurane-induced flow changes, the rise time in measured blood flow was calculated.
-Rise time was defined as the time elapsed following the start of anesthesia for $ICT$ values to increase by 50\% relative to the awake baseline.
-A spatially-resolved blood flow rise time map was generated for Subject 1 by performing this calculation pixel-wise across the entire field-of-view.
+Rise time was defined as the time elapsed following the start of anesthesia for flow values to increase by 50\% relative to the awake baseline.
+A spatially-resolved blood flow rise time map based on $ICT$ was generated for Subject 1 by performing this calculation pixel-wise across the entire field-of-view.
 Analogous rise time calculations were performed on the vascular flux and parenchymal tissue perfusion metrics across all subjects and imaging sessions using the previously extracted ROI timecourses.
@@
 \subsubsection{Statistical Analysis}
-All statistical analyses were performed using MATLAB (R2021a, MathWorks, Inc.).
-The differences between arteriole, venule, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons.
+All statistical analyses were also performed using MATLAB.
+The differences between arterial, venous, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons.
 $p \leq 0.05$ was considered statistically significant.
@@
 The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system}b and Video 1, which highlights the transition from the awake to the anesthetized state.
-The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane.
+The visible decrease in speckle contrast and corresponding increase in $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane.
 Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased.
@@
         (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$"$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.).
-(b) Single exposure LSCI (5 ms) and MESI inverse correlation time ($ICT$) during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG-4, 35.8 MB).
+(b) Single exposure LSCI (5 ms) and MESI during the awake and anesthetized states in Subject 1 (Scale bar = 1 mm).
+See Video 1 (MPEG-4, 29.8 MB) for the transition between each state during the induction of general anesthesia.
     }
@@
 The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia be reduced to 1.5\% isoflurane for several minutes.
-The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size.
+The breathing abnormality and change in anesthesia dosage had minimal effect on the vessel size.
 Repeated measurements in the subject (Figs.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
@@
 The anesthetized measurements for Subject 1, which underwent the extending imaging sessions, were taken at $t \approx 80$ minutes to match the timing of the other subjects (20 minutes after the start of anesthesia).
-A total of 108 measurements were included in the analysis (33 arteriole, 29 venule, 46 parenchyma).
+A total of 108 measurements were included in the analysis (33 arteries, 29 veins, 46 parenchyma regions).
 Similar to the results seen in Fig.~\ref{fig:timecourse}, the vasodilatory effects of isoflurane induced large changes in the cortical hemodynamics.
-On average, vessel width increased by 14.1\%, with arterioles increasing by 15.0\% and venules increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
-There was no significant difference in the percent change in width between arterioles and venules ($p = 0.61$).
-Vascular flux increased, on average, by 96.0\%, with arterioles increasing by 81.7\% and venules increasing by 112.2\% (Fig.~\ref{fig:aggregated}b).
+On average, vessel width increased by 14.1\%, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
+There was no significant difference in the percent change in width between arteries and veins ($p = 0.61$).
+Vascular flux increased, on average, by 96.0\%, with arteries increasing by 81.7\% and veins increasing by 112.2\% (Fig.~\ref{fig:aggregated}b).
 Parenchymal tissue perfusion increased by 84.7\%.
-While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arterioles, venules, and parenchyma were all non-significant ($p > 0.05$).
+While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arteries, veins, and parenchyma regions were all non-significant ($p > 0.05$).
 
@@
     \caption {
-        (a) Percent change in vessel diameter for arterioles and venules between awake and anesthetized states ($p > 0.05$).
-(b) Percent change in arteriolar and venous vascular flux and parenchymal tissue perfusion between awake and anesthetized states ($p > 0.05$).
+        (a) Percent change in vessel diameter for arteries and veins between the awake and anesthetized states ($p > 0.05$).
+(b) Percent change in arterial and venous vascular flux and parenchymal tissue perfusion between the awake and anesthetized states ($p > 0.05$).
 Measurements in both charts aggregated across all subjects and all imaging sessions.
@@
 $ICT$ values across the entire field-of-view increased by at least 50\% in just over one minute following the start of anesthesia.
-The vasculature, including both arterioles and venules, appears to change flow faster than the parenchyma.
-However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b), arterioles have significantly faster rise times ($40.5$ seconds) compared to venules ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma ($46.1$ seconds, $p = 0.006$).
-Parenchymal regions also have significantly faster rise times than venules ($p = 0.043$).
+The vasculature, including both arteries and veins, appears to change flow faster than parenchyma regions.
+However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b), arteries have significantly faster rise times ($40.5$ seconds) compared to veins ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma regions ($46.1$ seconds, $p = 0.006$).
+Parenchymal regions also have significantly faster rise times than veins ($p = 0.043$).
 
@@
     \caption {
-        (a) Blood flow rise time map depicting the time elapsed following the start of anesthesia for the inverse correlation time ($ICT$) to increase by 50\% relative to awake baseline in Subject 1 (Scale bar = 1 mm).
-(b) Time for arteriolar and venous vascular flux and parenchymal tissue perfusion to increase by 50\% relative to the awake baseline (***$p = \num{3.7e-6}$, **$p = 0.006$, *$p = 0.043$).
+        (a) Blood flow rise time map depicting the time elapsed following the start of anesthesia for $ICT$ to increase by 50\% relative to the awake baseline in Subject 1 (Scale bar = 1 mm).
+(b) Time for arterial and venous vascular flux and parenchymal tissue perfusion to increase by 50\% relative to the awake baseline (***$p = \num{3.7e-6}$, **$p = 0.006$, *$p = 0.043$).
 Measurements aggregated across all subjects and all imaging sessions.
@@
 The systemic effects of isoflurane undermine the reliability of neurophysiological and behavioral studies because anesthesia is a fundamentally unnatural physiological state \cite{Gao:2017tw}.
-Imaging blood flow on the cortical surface with LSCI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
-On average, the vasodilation caused by isoflurane increased vessel diameter by 14.1\% across all trials, with arterioles increasing by 15.0\% and venules increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
+Imaging blood flow on the cortical surface with MESI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
+On average, the vasodilation caused by isoflurane increased vessel diameter by 14.1\% across all trials, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
 Direct microscope measurements in fentanyl- and nitrous oxide-anesthetized rats documented a 17\% increase in arteriolar diameter and 6\% increase in venule diameter after the topical application of isoflurane \cite{Koenig:1994rn}.
@@
 The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so the results are not directly comparable \cite{Kazmi:2015du}.
-Another more recent study using Doppler OCT measured a 55\% increase in total (volumetric) blood flow in mice under isoflurane \cite{Rakymzhan.2021}.
+Another more recent study using Doppler OCT measured a 55\% increase in volumetric blood flow in mice under isoflurane \cite{Rakymzhan.2021}.
 Unlike the results presented above, this change was largely driven by vasodilation rather than an increase in blood flow velocity.
@@
 fMRI measurements in isoflurane-anesthetized rats have reported $\sim$50\% increases in global CBF with the cerebral cortex experiencing the smallest regional increase (20\%) compared to the awake state \cite{Sicard:2003dj}.
-However, these numbers are not directly comparable because fMRI samples a much larger volume of the brain than LSCI, which has both a smaller field-of-view and only penetrates several hundred microns into the cortex.
+However, these numbers are not directly comparable because fMRI samples a much larger volume of the brain than MESI, which has both a smaller field-of-view and only penetrates several hundred microns into the cortex.
 
 While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}.
-Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a small range of flow rates \cite{Parthasarathy:2008el}.
+Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a narrow range of flow rates \cite{Parthasarathy:2008el}.
 Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the surface vasculature.
@@
 The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:timecourse}b.
-This may result in extended imaging sessions documenting disparate anatomies and physiologies between the beginning and conclusion of an experiment.
+This could cause extended imaging sessions to document disparate anatomies and physiologies between the beginning and conclusion of an experiment.
 
@@
 Because the experiment imaged the induction of general anesthesia from the awake state, tracheal intubation for mechanical ventilation was not an option.
-This may result in breathing variability that impacts the systemic hemodynamics and complicates comparisons with other studies that had mechanical control of ventilation.
+This may have resulted in breathing variability that impacted the systemic hemodynamics and complicated comparisons with other studies that had mechanical control of ventilation.
 Since varying the isoflurane dosage was the only method of regulating breathing stability, the concentration dependent effects of isoflurane may have also influenced the results \cite{Masamoto:2009dd,Li:2014eh}.
@@
 While image registration can help maintain the spatial alignment of data across an experiment, it is unable to decouple the effects of animal motion from the underlying blood flow.
-Even with the head fully restrained, walking and grooming both cause subtle brain movements that manifest as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:timecourse}c.
+Even with the head fully restrained, walking and grooming both caused subtle brain movements that manifested as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:timecourse}c.
 While these fluctuations may represent real hemodynamic responses, it is difficult to isolate them from broader animal motion.
-A simple solution might be the addition of an external sensor to the treadmill \cite{Dombeck:2007gr} to exclude timepoints when the animal is actively moving.
+A simple solution might be the addition of an external sensor to the treadmill to exclude timepoints when the animal is actively moving \cite{Dombeck:2007gr}.
 However, a more refined awake imaging system that further minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI or MESI.
@@
 These increases in vessel size and blood flow were repeatable across multiple imaging sessions and subjects.
-This study also demonstrated that MESI can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
+We also documented disparate response times to the induction of isoflurane anesthesia between arteries, veins, and parenchyma regions.
+This study demonstrated that MESI can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
 These results provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.

### 2021-08-18 article.tex
Updates for journal requirements
- Include ARRIVE guidelines
- Declaration of Interest
- CRediT Statement

@@
 cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}.
-All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.
+All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals in compliance with ARRIVE guidelines and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.
 
@@
 
-\section*{Disclosures}
+\section*{Declaration of Interest}
 A.K.D. holds equity in Dynamic Light, Inc. The authors declare no other conflicts of interest.
 
-\section*{Author Contributions}
-C.T.S.
-and L.M.R.
-constructed the imaging system, conceived the experiments, and acquired the data.
-C.T.S analyzed the results and wrote the manuscript.
-F.H.
-performed the animal surgeries.
-L.L.
-and A.K.D.
-supervised the project.
-All authors contributed to the manuscript revisions.
+\section*{CRediT Statement}
+\textbf{Colin T.
+Sullender:} Conceptualization, Methodology, Software, Validation, Investigation, Data Curation, Formal Analysis, Writing - Original Draft, and Visualization.
+\textbf{Lisa M.
+Richards:} Conceptualization, Methodology, Investigation, Data Curation, Writing - Review \& Editing.
+\textbf{Fei He:} Investigation, Resources, Writing - Review \& Editing.
+\textbf{Lan Luan:} Writing - Review \& Editing, Supervision, and Funding Acquisition.
+\textbf{Andrew K.
+Dunn:} Conceptualization, Writing - Review \& Editing, Supervision, Funding Acquisition, and Project Administration.
 

### 2021-08-19 article.tex
Standardized CRediT formatting

@@
 \textbf{Lisa M.
-Richards:} Conceptualization, Methodology, Investigation, Data Curation, Writing - Review \& Editing.
-\textbf{Fei He:} Investigation, Resources, Writing - Review \& Editing.
+Richards:} Conceptualization, Methodology, Investigation, Data Curation, and Writing - Review \& Editing.
+\textbf{Fei He:} Investigation, Resources, and Writing - Review \& Editing.
 \textbf{Lan Luan:} Writing - Review \& Editing, Supervision, and Funding Acquisition.

### 2021-10-26 article.tex
Remove journal name
Response to Reviewer #1

@@
 Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
-The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}).
+The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast images across each exposure time, and computing the corresponding MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
 A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%).
@@
 After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
-The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames.
+The pulse oximeter was also attached and used to monitor vitals and regulate the depth of anesthesia such that the heart rate was matched to within 10\% between imaging sessions for each subject \cite{Kazmi:2013hp}.
+The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring an additional 50 MESI frames.
+The speckle contrast images were then averaged across each exposure time and used to compute the MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
 The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage.
@@
 
+The correction for multiple dynamic scattering events applied to the vascular MESI measurements cannot be directly translated to the parenchyma regions \cite{Kazmi:2015du}.
+Therefore all parenchyma MESI measurements assume only a single dynamic scattering event per photon, which is not a reliable representation of the underlying dynamics \cite{Davis:2015ij}.
+Recent efforts to directly measure the intensity autocorrelation function have produced a modified speckle contrast model that assumes both multiple scattering and unordered dynamics \cite{Postnov.2020}.
+Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are significant reductions in flow.
+
 % ----------------------------------------------------------------------------------------
@@
 % ----------------------------------------------------------------------------------------
-\bibliography{bibliography.bib}
+\bibliography{bibliography}
 \bibliographystyle{elsarticle-num}

### 2021-10-27 article.tex
Response to Reviewer #2 (Partial)

@@
 Camera exposures were temporally synchronized with the modulated laser pulses.
-Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
+Fifteen camera exposures spanning three orders of magnitude (0.05, 0.075, 0.1, 0.25, 0.5, 0.75, 1.0, 2.5, 5.0, 7.5, 10, 25, 40, 50, and 80 ms) \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second.
 The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}.
@@
 Recent efforts to directly measure the intensity autocorrelation function have produced a modified speckle contrast model that assumes both multiple scattering and unordered dynamics \cite{Postnov.2020}.
-Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are significant reductions in flow.
+Applying this correction could improve the robustness of the MESI measurements in parenchyma regions, particularly when there are major changes in flow.
 

### 2021-10-28 article.tex
Response to Reviewer #3

@@
 Volatile inhalation anesthetics, such as the halogenated ether isoflurane \cite{Eger:1981ia}, are commonly utilized to immobilize animals during imaging while allowing for fine control over the depth of anesthesia and consciousness.
-However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Iida:1998th}.
+However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea}, interfere with functional connectivity at higher doses \cite{Xie:2019de}, and suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}.
 Isoflurane also conveys potential neuroprotective effects that reduce and delay the severity of cerebral ischemia \cite{Kitano:2007ia,Kawaguchi:2000id,Sakai:2007wc,Li:2013ip,Lu:2017bo}.
@@
 The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging.
-They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear treadmill awake imaging system \cite{He:2020}.
+They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a custom, low-profile linear treadmill system \cite{He:2020}.
 
@@
 Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes.
-The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast images across each exposure time, and computing the corresponding MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
+Periods of extended locomotion on the treadmill were manually noted throughout the experiment.
+The awake hemodynamic baseline was defined by acquiring 50 MESI frames, averaging the speckle contrast images across each exposure time, and computing the corresponding MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
 A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%).
@@
 After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature.
-The pulse oximeter was also attached and used to monitor vitals and regulate the depth of anesthesia such that the heart rate was matched to within 10\% between imaging sessions for each subject \cite{Kazmi:2013hp}.
+A pulse oximeter (MouseSTAT, Kent Scientific Corp.) was also attached and used to monitor vitals and regulate the depth of anesthesia such that the heart rate was matched to within 10\% between imaging sessions for each subject \cite{Kazmi:2013hp}.
 The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring an additional 50 MESI frames.
@@
 Even with the head fully restrained, walking and grooming both caused subtle brain movements that manifested as large changes in speckle contrast, as seen by the abrupt spikes during the awake section of Fig.~\ref{fig:timecourse}c.
-While these fluctuations may represent real hemodynamic responses, it is difficult to isolate them from broader animal motion.
-A simple solution might be the addition of an external sensor to the treadmill to exclude timepoints when the animal is actively moving \cite{Dombeck:2007gr}.
-However, a more refined awake imaging system that further minimizes brain movement would likely be necessary to directly probe these phenomena with LSCI or MESI.
+While these fluctuations may represent real hemodynamic responses, it is difficult to isolate them from broader animal motion given LSCI's inherent sensitivity to any movement \cite{Richards:2014kx}.
+A simple solution might be the addition of an external sensor to the treadmill to automatically exclude timepoints when the animal is actively moving \cite{Dombeck:2007gr}.
+Alternatively, a webcam could be used to monitor all animal activity, which could facilitate comparisons between animals at rest, grooming, or locomoting.
+However, a more refined awake imaging system that further minimizes brain movement may likely be necessary to directly probe these phenomena with LSCI or MESI.
 
@@
 This study demonstrated that MESI can be readily used for chronic awake imaging and allows for direct day-to-day comparisons of blood flow.
-These results provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.
+There are numerous applications for the longitudinal characterization of CBF dynamics in studying the progression of ischemic stroke absent the effects of anesthesia and the efficacy of potential therapeutics targeting flow restoration.
+These results also provide further evidence that the anesthetized state is unrepresentative of normal physiology and that neurophysiological and behavioral experiments would benefit immensely from transitioning to un-anesthetized awake animal models.
 

### 2021-10-28 article.tex
Report F-statistic with ANOVAs

@@
 On average, vessel width increased by 14.1\%, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
-There was no significant difference in the percent change in width between arteries and veins ($p = 0.61$).
+There was no significant difference in the percent change in width between arteries and veins ($F_{(1,60)} = 0.27$, $p = 0.61$).
 Vascular flux increased, on average, by 96.0\%, with arteries increasing by 81.7\% and veins increasing by 112.2\% (Fig.~\ref{fig:aggregated}b).
 Parenchymal tissue perfusion increased by 84.7\%.
-While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arteries, veins, and parenchyma regions were all non-significant ($p > 0.05$).
+While the one-way ANOVA was significant ($F_{(2,105)} = 0.27$, $p = 0.041$), the multiple pairwise comparisons between arteries, veins, and parenchyma regions were all non-significant ($p > 0.05$).
 
@@
         (a) Percent change in vessel diameter for arteries and veins between the awake and anesthetized states ($p > 0.05$).
-(b) Percent change in arterial and venous vascular flux and parenchymal tissue perfusion between the awake and anesthetized states ($p > 0.05$).
+(b) Percent change in arterial and venous vascular flux and parenchymal tissue perfusion between the awake and anesthetized states (Pairwise comparisons all $p > 0.05$).
 Measurements in both charts aggregated across all subjects and all imaging sessions.
@@
 The vasculature, including both arteries and veins, appears to change flow faster than parenchyma regions.
-However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b), arteries have significantly faster rise times ($40.5$ seconds) compared to veins ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma regions ($46.1$ seconds, $p = 0.006$).
-Parenchymal regions also have significantly faster rise times than veins ($p = 0.043$).
+However, upon aggregating ROI measurements across all subjects and imaging sessions (Fig.~\ref{fig:risetime}b) and finding a statistically significant one-way ANOVA ($F_{(2,105)} = 13.4$, $p = \num{6.5e-6}$), arteries have significantly faster rise times ($40.5$ seconds) compared to veins ($50.7$ seconds, $p = \num{3.7e-6}$) or parenchyma regions ($46.1$ seconds, $p = 0.006$).
+Parenchyma regions also have significantly faster rise times than veins ($p = 0.043$).
 

### 2021-11-04 article.tex
Response to Reviewer #2

@@
 \usepackage[version=4]{mhchem}
+\usepackage{booktabs}
 
@@
 All statistical analyses were also performed using MATLAB.
+Paired sample t-tests were used to compare awake and anesthetized measurements across vessel diameter and CBF metrics.
 The differences between arterial, venous, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons.
-$p \leq 0.05$ was considered statistically significant.
+The significance level ($\alpha$) was set to 0.05 for all statistical tests.
 
@@
 The breathing abnormality and change in anesthesia dosage had minimal effect on the vessel size.
-Repeated measurements in the subject (Figs.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
+Repeated measurements in the subject (Fig.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.
 
@@
 \end{figure}
+
+The differences between awake and anesthetized measurements across vessel diameter and CBF metrics are summarized in Table \ref{tab:awakeanes}.
+Paired samples t-tests were performed on data aggregated across all subjects and imaging sessions in each state.
+Paired measurements from 33 arteries, 29 veins, and 46 parenchyma regions were included in the analysis.
+There were significant differences between the awake and anesthetized measurements for all tested metrics.
+
+% Table 1 - Aggregated Awake vs. Anesthetized Summary
+\begin{table}[]
+    \caption {
+        Paired samples t-tests comparing differences between awake and anesthetized measurements across vessel diameter and blood flow metrics ($\alpha = 0.05$).
+    }
+    \label{tab:awakeanes}
+    \centering
+    \begin{tabular}{llccc} 
+        \addlinespace
+        \toprule
+        \textbf{Metric} & \textbf{Region}  & \textbf{$\boldsymbol{t}$} & \textbf{$\boldsymbol{df}$} & \textbf{$\boldsymbol{p}$} \\
+        \midrule
+        Vessel Dia.     & Artery ($\mu$m)  & -6.15                     & 32                         & $\num{7.1e-7}$            \\
+                        & Vein ($\mu$m)    & -3.67                     & 28                         & 0.001                     \\
+        \midrule
+        Blood Flow      & Artery (Flux)    & -10.75                    & 32                         & $\num{3.7e-12}$           \\
+                        & Vein (Flux)      & -4.96                     & 28                         & $\num{3.1e-5}$            \\
+                        & Parenchyma (ICT) & -18.44                    & 45                         & $\num{1.3e-22}$           \\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%.
-The repeatability of the day-to-day measurements shown in Figs.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
+The repeatability of the day-to-day measurements shown in Fig.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
 

### 2021-11-04 article.tex
Minor edits

@@
 A circular region (4 mm diameter) of the skull including the dura mater over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion.
-A 4 mm round \#1.5 cover glass (World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
+A 4 mm round cover glass (\#1.5, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void.
 Gentle pressure was applied to the cover glass while Kwik-Sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull.
@@
 The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging.
-They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a custom, low-profile linear treadmill system \cite{He:2020}.
+They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a custom low-profile linear treadmill system \cite{He:2020}.
 
@@
 The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring an additional 50 MESI frames.
-The speckle contrast images were then averaged across each exposure time and used to compute the MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
+The speckle contrast images were then averaged across each exposure time and used to compute the anesthetized MESI $ICT$ image using Eq.~(\ref{eq:mesi}).
 The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage.
@@
 All data processing was performed using MATLAB (R2021a, MathWorks, Inc.).
-While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts.
+While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate all motion.
 The induction of general anesthesia also causes major changes in posture that can result in lateral displacements of the brain relative to the skull.
@@
 The vascular flux was then computed by scaling the $ICT$ by $d_{vessel}$ at each timepoint.
-The percent change in vessel diameter and vascular flux were calculated using the average of the entire awake state for the baseline.
+The percent change in vessel diameter and vascular flux were calculated using the average of the entire awake timecourse for the baseline.
 
@@
 \subsubsection{Statistical Analysis}
-All statistical analyses were also performed using MATLAB.
+All statistical analyses were performed using MATLAB.
 Paired sample t-tests were used to compare awake and anesthetized measurements across vessel diameter and CBF metrics.
@@
     \caption {
-        Paired samples t-tests comparing differences between awake and anesthetized measurements across vessel diameter and blood flow metrics ($\alpha = 0.05$).
+        Paired samples t-tests comparing differences between awake and anesthetized measurements of aggregated vessel diameter and blood flow metrics ($\alpha = 0.05$).
     }
@@
 The systemic effects of isoflurane undermine the reliability of neurophysiological and behavioral studies because anesthesia is a fundamentally unnatural physiological state \cite{Gao:2017tw}.
-Imaging blood flow on the cortical surface with MESI during the induction of anesthesia directly visualizes and quantifies these large hemodynamic changes.
+Imaging blood flow on the cortical surface with MESI during the induction of anesthesia directly visualizes and quantifies these large acute hemodynamic changes.
 On average, the vasodilation caused by isoflurane increased vessel diameter by 14.1\% across all trials, with arteries increasing by 15.0\% and veins increasing by 13.0\% (Fig.~\ref{fig:aggregated}a).
@@
 Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the surface vasculature.
-Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%.
+For example, using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:timecourse}c would have measured only a 141\% increase in the large vessel instead of 270\%.
 The repeatability of the day-to-day measurements shown in Fig.~\ref{fig:timecourse}d-f further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.
